### 2017-06-09 paper/manuscript.tex
initial commit

\documentclass{sbrt2013port}
%\usepackage[brazil]{babel}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{color}
%\usepackage{placeins}
\usepackage{bm}
%\usepackage{cite}
%\usepackage{stfloats}
%\usepackage{float}
\usepackage{hyperref}
%\usepackage{cite}
\usepackage{tabularx,colortbl}

\begin{document}

\title{Simulating Generalized Fading Channels in Python}

\author{José Vinícius de M. Cardoso$^1$,   Paulo Ribeiro Lins Júnior$^2$, Wamberto Queiroz$^1$ e Marcelo Sampaio de Alencar$^3$
\thanks{\noindent Instituto de Estudos Avançados em Comunicações -- Iecom; $^1$Universidade Federal de Campina Grande -- UFCG; $^2$Grupo de Pesquisa em Comunicações e Processamento de Informação -- GComPI/Instituto Federal de Educação, Ciência e Tecnologia da Paraíba -- IFPB, Campus Campina Grande -- PB, $^3$Universidade Federal da Bahia -- UFBA, emails: $^1$\{josevinicius, wamberto\}@iecom.org.br, $^2$paulo.lins@ifpb.edu.br e $^3$malencar@iecom.org.br.}}

\maketitle

\markboth{XXXVI SIMPÓSIO BRASILEIRO DE TELECOMUNICAÇÕES E PROCESSAMENTO DE SINAIS - SBrT'2018, 16-19 DE SETEMBRO DE 2018, CAMPINA GRANDE, PB} {XXXVI SIMPÓSIO BRASILEIRO DE TELECOMUNICAÇÕES E PROCESSAMENTO DE SINAIS - SBrT'2018, 16-19 DE SETEMBRO DE 2018, CAMPINA GRANDE, PB}

\begin{abstract}
    We present a novel and well tested Python-based library for simulating and computing
    generalized fading channels, considering $\alpha\text{-}\mu$, $\kappa\text{-}\mu$, and
$\eta\text{-}\mu$ distributions. We describe the
    applicability of this library using a few communications channels scenarios
    impaired by generalized fading, namely, spectrum sensing and bit error
    rate computation. The development of the library is open source and its code, along
    with examples, are available at
    \texttt{http://github.com/mirca/maoud}.
\end{abstract}

\begin{keywords}
Generalized Fading, Simulation, Python
\end{keywords}

\section{Introduction}

The study of modern wireless communications systems heavily relies on fading channel simulation.
By fading channel simulation, we refer to the generation of samples from a probability distribution
that resembles the effects and impairments caused by real communications fading channels on the
transmitted signal.

Although accurate and precise distributions for generalized fading have been
estabilished in the literature, such as $\alpha\text{-}\mu$~\cite{yacoub.2007.1},
$\kappa\text{-}\mu$~\cite{yacoub.2007.2} and $\eta\text{-}\mu$~\cite{yacoub.2007.2},
the generation of samples following these distributions is usually
a time-consuming task.

In~\cite{cogliatti2012}, the authors built an efficient
algorithm, based on the rejection method, for generation of samples from those
distributions. However, there are neither open nor
closed source implementations available to the scientific community.

In this paper, we present an open source Python package
for generation of samples following the $\alpha\text{-}\mu$, $\kappa\text{-}\mu$, and
$\eta\text{-}\mu$ distributions. The usefullness of ths package is illustrated
through well known examples involving spectrum sensing and bit error rate (BER) computation.

\section{Rejection Sampling}\label{rejec}

The algorithm implemented in this work, originally proposed in~\cite{cogliatti2012},
is based on the rejection method, which is one of the most used for the generation
of samples of a probability distribution.

We briefly describe the algorithm as follows. Consider that we would like to simulate a
random variable $x$ with a probability density $f$. The basic idea is to find
an alternative probability density $g$, from which there exists an efficient procedure
to generate samples, e.g., inverse methods. Additionally, it is required that $g$
majorizes $f$, i.e., we assume that there exists a real number $c$ such that $f(x)/g(x) < c$.

Basically, the steps of the rejection algorithm are~\cite{ross}:
\begin{enumerate}
	\item generate a sample $y$ from the probability density $g$;
    \item generate a sample $u$ from a uniform density with support $(0, 1)$;
	\item check $u \leq \frac{f(y)}{cg(y)}$; if true then accept $y$; otherwise, return to step 1.
\end{enumerate}

The implementation of this algorithm along with the code to efficiently generate
samples from the $\alpha$-$\mu$, $\eta$-$\mu$, and $\kappa$-$\mu$ distributions
is available at \url{http://github.com/mirca/maoud}.

In order to validate the implementation, we apply the routines to
two use cases in wireless communications: spectrum sensing and bit error rate computation.

\section{Spectrum Sensing in Complex Generalized Fading Channels}~\label{sensing}

The spectrum sensing problem consists in deciding whether or not a given channel
frequency band is being occupied by a licensed (primary) user and, in case that such
frequency band is available, how to opportuniscally allocate secondary users
such that the interference on the primary user is negligible.

From a probabilistic point of view, the spectrum sensing problem may be framed as
a decision theory problem, as follows
\begin{align}
    H_0:  \bm{y} &= \bm{w},\\
    H_1:  \bm{y} &= h\bm{s} + \bm{w},
\end{align}
\noindent in which $\bm{y} \in \mathbb{C}^{n\times 1}$ is the received vector signal,
$\bm{w} \in \mathbb{C}^{n\times 1}$ is complex Gaussian noise process with zero mean
vector and covariance matrix given as $\sigma^2\bm{I}_n$, and $h$ is the channel gain.

In~\cite{cardoso2017}, the authors have shown that the cumulative distribution function (cdf) of the
energy statistic $\tilde{y} \triangleq \bm{y}^{\dagger}\bm{y}$ conditioned on the knowledge of $h$,
in case that $\bm{s}$ is an $M$-PSK signal such that every symbol has the same probability of occurrence,
$\mathbb{P}(s_n = s) = \frac{1}{M}$, is given as
\begin{align}
    P(\tilde{y} | h, H_1) = 1 - \mathrm{Q}_{n}\left(\sqrt{\dfrac{2n|h|^2E_s}{\sigma^2}}, \sqrt{\dfrac{2\tilde{y}}{\sigma^2}}\right),
\end{align}
in which $\mathrm{Q}_{n}$ is the Marcum-$\mathrm{Q}$ function and $E_s$ is the energy per symbol.

Recall that the energy detection rule can be expressed as
\begin{equation}
    d_\delta (\tilde{y}) = \mathbb{I}(\tilde{y} > \delta)
\end{equation}
in which $\mathbb{I}$ is the indicator function, $\delta$ is a strictly positive real
number known as energy threshold, and $d_\delta (\tilde{y}) = j,~j \in \{0,1\}$,
means that the detector has decided in favor of the hypothesis $H_j$.

As a result, the probabilities of false alarm and miss detection can
be written as
\begin{align}
    \mathbb{P}\left(d_\delta(\tilde{y}) = 1 | H_0\right) &=
        1 -  P(\delta | H_0) = 1 - \gamma\left(n, \frac{\delta}{\sigma^2}\right),\label{eq:pf} \\
    \mathbb{P}\left(d_\delta(\tilde{y}) = 0 | H_1\right) & = \int_{-\infty}^{+\infty} P(\delta | h, H_1)p(h)\;\mathrm{d}h,\label{eq:pd}
\end{align}
in which $\gamma$ is the regularized lower incomplete Gamma function, $p(h)$ is the pdf of the fading,
and $\delta$ is the energy detection threshold.

The performance of detection schemes can be measured by computing the Receiver Operating
Characteristic (ROC), which consists in varying $\delta$ and computing the pairs of
probability of false alarm and miss detection, as illustrated in Fig.~\ref{fig:spectrum-sensing}, in which the solid curve represents the theorectical probabilities as stated on
(\ref{eq:pf}) and (\ref{eq:pd}) for different values of
$\delta$, whereas bullets represent Monte Carlo simulations acquired with $10^6$ realizations.
The input signal $\bm{s}$ consists in a vector of length $n=25$ in which each entry represents
a symbol of a 64-PSK constellation. Symbols are assumed to be equiprobable and
the signal-to-noise ratio is set to $5$ dB.

\begin{figure}[!htb]
    \centering
    \includegraphics{figures/spectrum_sensing}
    \caption{Receiver Operating Characteristic for the energy detector in $\alpha$-$\mu$
             channel with $\alpha=2$ and $\mu=1$.
             }
    \label{fig:spectrum-sensing}
\end{figure}

\section{Bit Error Rate in $\alpha$-$\mu$ Fading}~\label{ber}

Consider the system
\begin{align}
    y = hs + w
\end{align}
in which $s \in \{0, a\}$, $a \in \mathbb{R}_{+}$, is a transmitted signal,
$h$ is an $\alpha$-$\mu$ random variable and $\bm{w}$ is a Gaussian random variable
with zero mean vector and variance $\sigma^2$, and $y$ is the received signal.

Assume that the binary symbols are equiprobable, then the probability of one bit error
is given as
\begin{align}
    p_{e} = \dfrac{1}{2}\left(\mathbb{P}\left(\hat{y} = 0 | s = a\right)
                            + \mathbb{P}\left(\hat{y} = 1 | s = 0\right)\right).
\end{align}

Further, assume that the decoded bit $\hat{y}$ is estimated using the minimum distance decoding
rule, i.e.,
\begin{align}
    \hat{y} = \mathbb{I}(|y - a|^2 < |y|^2)
\end{align}
therefore
\begin{align}
    \mathbb{P}\left(\hat{y} = 1 | s = 0\right) & = \mathbb{P}\left(|w - a|^2 - |w|^2 < 0\right) = 1 - \Phi\left(\frac{a}{2\sigma}\right)
\end{align}
and likewise
\begin{align}
    \mathbb{P}\left(\hat{y} = 0 | s = a\right) & = \mathbb{P}\left(ha + w < \frac{a}{2}\right) = \mathbb{E}_h\left(\Phi\left(\frac{a(1 - 2h)}{2\sigma}\right)\right).
\end{align}

In Fig.~\ref{fig:ber}, we show the expression of the BER as a function of the signal-to-noise ratio,
for the system under consideration with $\alpha=2$ and $\mu = 5$.
As we can see, the simulation presents an excellent agreement against theorectical results.
\begin{figure}[!htb]
    \centering
    \includegraphics{figures/ber}
    \caption{BER as a function of the SNR for $\alpha=2$ and $\mu = 5$}
    \label{fig:ber}
\end{figure}

\section{Conclusions}\label{conclusions}

This paper presents a novel Python-based library for generalized fading simulation.
The implementation is tested and validated in two use cases, namely,
spectrum sensing and BER computation.

The computational results show that the implementation presents a
satisfactory agreement when compared with the theorectical formulation.

We expect that the proposed library, which is open source,
will be usefull to researchers, professors, and students of
the field of wireless communications.

Finally, all the simulations were done in a personal laptop,
and the generation of $10^6$ samples from any of the generalized fading
distributions took on average 10 seconds.

\bibliographystyle{IEEEtran}
\bibliography{manuscript}

\end{document}

### 2017-06-09 sampling.py
update docs and gitignore

@@ -2,6 +2,9 @@ import numpy as np
 
 def rejection_sampling(pdf, low, high, n_samples, *args):
     """
+    This is a not-very-efficient implementation of the acceptance-rejection
+    sampler. (I don't know why I even put it on github).
+
     Parameters
     ----------
     pdf : callable
@@ -12,6 +15,11 @@ def rejection_sampling(pdf, low, high, n_samples, *args):
         Number of desired samples
     args : list
         List of additional arguments to be passed to ``pdf``.
+
+    Returns
+    -------
+    accepted_samples : array
+        Array containing samples from ``pdf``
     """
 
     x = np.linspace(low, high, n_samples)

### 2017-06-10 sampling.py
add example notebook

@@ -31,10 +31,10 @@ def rejection_sampling(pdf, low, high, n_samples, *args):
     n_accepted_samples = 0
     accepted_samples = []
     while n_accepted_samples < n_samples:
-        unif_x = np.random.uniform.rvs(low=low, high=high, size=n_samples)
-        unif_y = np.random.uniform.rvs(size=n_samples)
+        unif_x = np.random.uniform(low=low, high=high, size=n_samples)
+        unif_y = np.random.uniform(size=n_samples)
         accept = np.where(unif_y <= pdf(unif_x, *args) / pdfmax)[0]
-        accepted_samples = np.concatenate([accepted_rvs, unif_x[accept]])
+        accepted_samples = np.concatenate([accepted_samples, unif_x[accept]])
         n_accepted_samples = accepted_samples.size
 
     return accepted_samples[:n_samples]

### 2018-03-04 yacoub/distributions.py
improve examples and sampler

@@ -1,8 +1,9 @@
 from abc import ABC, abstractmethod
 import numpy as np
+import math
 import scipy.special as sps
 import scipy.stats as stats
-from sampling import rejection_sampling
+from .sampling import rejection_sampling
 
 
 class Distribution(ABC):
@@ -38,7 +39,7 @@ class Distribution(ABC):
         return rejection_samples(self.pdf, low, high, size)
 
 
-class ComplexDistributions(Distribution):
+class ComplexDistribution(Distribution):
     """Defines a class for probability distribution
     arising from a complex random variable Z = X + jY,
     where j = sqrt(-1).
@@ -97,9 +98,9 @@ class EtaMu(Distribution):
 
     def pdf(self, x):
         return (4.0 * np.sqrt(np.pi) * self.mu ** (self.mu + 0.5) * x ** (2 * self.mu)
-                * np.exp(-2.0 * self.mu * x * x / (1.0 + self.eta))
-                * sps.ive(self.mu - 0.5, 2.0 * self.eta * self.mu * x * x / (1.0 - self.eta * self.eta))
-                / (self.eta ** (self.mu - 0.5) * np.sqrt(1.0 - self.eta * self.eta)
+                * np.exp(-2. * self.mu * x * x / (1. + self.eta))
+                * sps.ive(self.mu - 0.5, 2. * self.eta * self.mu * x * x / (1. - self.eta * self.eta))
+                / (self.eta ** (self.mu - 0.5) * np.sqrt(1. - self.eta * self.eta)
                 * sps.gamma(self.mu)))
 
 
@@ -109,11 +110,12 @@ class KappaMu(Distribution):
         self.mu = mu
 
     def pdf(self, x):
-	return (2.0 * self.mu * (1.0 + self.kappa) ** ((self.mu + 1.0) / 2.0) * x ** self.mu
-                * np.exp(-self.mu * (1 + self.kappa) * x * x - self.mu * self.kappa + 2 * x * self.mu
-                * np.sqrt(self.kappa * (1 + self.kappa)))
-                * sps.ive(self.mu - 1, 2 * self.mu * x * np.sqrt(self.kappa * (1.0 + self.kappa)))
-                / (self.kappa ** ((self.mu - 1.0) / 2.0)))
[…]

### 2018-03-04 yacoub/sampling.py

@@ -1,6 +1,7 @@
 import numpy as np
+import math
 
-def rejection_sampling(pdf, low, high, n_samples, *args):
+def rejection_sampling(pdf, x, n_samples, *args):
     """
     This is actually a pretty good implementation of the acceptance-rejection
     sampler.
@@ -9,10 +10,10 @@ def rejection_sampling(pdf, low, high, n_samples, *args):
     ----------
     pdf : callable
         The analytical formulation of the density function to get samples from.
-    low, high : float, float
-        The support of the density or the interval where to get samples.
+    x : array
+        The support of the pdf.
     n_samples : int
-        Number of desired samples
+        The sample size.
     args : list
         List of additional arguments to be passed to ``pdf``.
 
@@ -21,18 +22,20 @@ def rejection_sampling(pdf, low, high, n_samples, *args):
     accepted_samples : array
         Array containing samples from ``pdf``
     """
+    pdf_x = pdf(x, *args)
+    pdf_min, pdf_max  = np.min(pdf_x), np.max(pdf_x)
 
-    x = np.linspace(low, high, n_samples)
-    pdfmax = np.max(pdf(x, *args))
-
-    if np.isnan(pdfmax) or np.isinf(pdfmax):
+    if not np.isfinite(pdf_max):
         raise ValueError("pdf has nan or inf values.")
 
+    n_samples = int(n_samples)
+    x_min, x_max = np.min(x), np.max(x)
     accepted_samples = []
-    while accepted_samples.size < n_samples:
-        unif_x = np.random.uniform(low=low, high=high, size=n_samples)
-        unif_y = np.random.uniform(size=n_samples)
-        accept = np.where(unif_y <= pdf(unif_x, *args) / pdfmax)[0]
+
+    while len(accepted_samples) < n_samples:
+        unif_x = np.random.uniform(low=x_min, high=x_max, size=n_samples)
+        unif_y = np.random.uniform(low=pdf_min, high=1., size=n_samples)
+        accept = np.log(unif_y) <= (np.log(pdf(unif_x, *args)) - math.log(pdf_max))
         accepted_samples = np.concatenate([accepted_samples, unif_x[accept]])
 
     return accepted_samples[:n_samples]

### 2018-03-04 yacoub/distributions.py
improve all

@@ -25,18 +25,18 @@ class Distribution(ABC):
         """
         pass
 
-    def rvs(self, low, high, size):
+    def rvs(self, x, size):
         """Returns a sample of length `size` in the range
-        [low, high].
+        [x.min(), x.max()].
 
         Parameters
         ----------
-        low, high : float, float
-            Lower and upper bounds to constrain the pdf.
+        x : array
+            The support of the pdf.
         size : int
             Size of the sample (number of realizations).
         """
-        return rejection_samples(self.pdf, low, high, size)
+        return rejection_samples(self.pdf, x, size)
 
 
 class ComplexDistribution(Distribution):
@@ -44,19 +44,24 @@ class ComplexDistribution(Distribution):
     arising from a complex random variable Z = X + jY,
     where j = sqrt(-1).
     """
-    def rvs(self, low, high, size):
+    def rvs(self, x, y, size):
         """Returns a sample of length `size` in the range
-        [low, high].
+        [x.min(), x.max()] and [y.min(), y.max()] for the
+        real and imaginary parts.
 
         Parameters
         ----------
-        low, high : float, float
-            Lower and upper bounds to constrain the pdf.
+        x, y : arrays
+            The support of the pdf of the real and imaginary parts,
+            respectively.
         size : int
             Size of the sample (number of realizations).
         """
-        return (rejection_samples(self.pdf, low, high, size)
-                + 1j * rejection_samples(self.pdf, low, high, size))
+        if len(x) != len(y):
+            raise ValueError("x and y must have the same length.")
+
+        return (rejection_samples(self.pdf, x, size)
+                + 1j * rejection_samples(self.pdf, y, size))
 
 
 class AlphaMu(Distribution):
@@ -92,6 +97,16 @@ class AlphaMu(Distribution):
 
 
 class EtaMu(Distribution):
+    """Defines the \eta — μ probability distribution.
+    For the theorectical aspects of the \eta — μ distribution, see
+    [ADD REFERENCE]
+
+    Attributes
+    ----------
+    eta, mu : float, float
+        Parameters that define the eta — μ distribution.
+    """
+
[…]

### 2018-03-04 paper/yacoub.tex
add setup.py

\documentclass[conference, 10pt]{IEEEtran}
\usepackage[cmex10]{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{color}
\usepackage{placeins}
%\usepackage{stfloats}
\usepackage{float}
\usepackage{hyperref}
\usepackage{cite}
\usepackage{tabularx,colortbl}

\begin{document}
\title{\texttt{yacoub}: a Python package for Simulating Generalized Fading Channels}

\author{\IEEEauthorblockN{Jos\'e~V.~de~M.~Cardoso,~Paulo~R.~Lins~Jr,~Wamberto~J.~L.~Queiroz,
                          ~and~Marcelo~S.~Alencar,~\textit{IEEE Senior Member}}
\IEEEauthorblockA{Universidade Federal de Campina Grande\\
Campina Grande, Para\'iba, Brazil\\
\{josevinicius,paulo,wamberto,malencar\}@iecom.org.br\\}
}

\maketitle

\begin{abstract}
    We present a well tested Python-based library for simulating and computing
    generalized fading channels, named \texttt{yacoub}. We describe the
    applicability of \texttt{yacoub} using examples in recent communications
    system, namely: cooperative spectrum sensing, bit error rate computation
    in generalized fading, and free space optics. The development of \texttt{yacoub}
    open source and its code is avaliable at \texttt{http://github.com/mirca/yacoub}.
\end{abstract}

\IEEEpeerreviewmaketitle
\section{Introduction}

\section{The Acceptance-Rejection sampler in log-space}

\section{Examples}
\subsection{Signal detection}
\subsection{Free Space Optics}
\subsection{BER in $\alpha-\mu$ Fading}

\section{Conclusions}

\section*{Acknowledgement}
The authors would like to thank the Federal University of Campina Grande (UFCG)
and the Institute for Advanced Studies in Communications (Iecom).

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,aps2016_regular.bib}

\end{document}

### 2018-03-04 setup.py

@@ -1,0 +1,41 @@
+#!/usr/bin/env python
+import sys
+from setuptools import setup
+# To use a consistent encoding
+from codecs import open
+import os
+from os import path
+
+# Prepare and send a new release to PyPI
+if "release" in sys.argv[-1]:
+    os.system("python setup.py sdist")
+    os.system("twine upload dist/*")
+    os.system("rm -rf dist/yacoub*")
+    sys.exit()
+
+here = path.abspath(path.dirname(__file__))
+
+# Get the long description from the README file
+with open(path.join(here, 'README.rst'), encoding='utf-8') as f:
+    long_description = f.read()
+
+setup(
+    name='yacoub',
+    packages=['yacoub'],
+    version='0.1.dev0',
+    description='A colorful, long-tailed package for beautiful Majorization-minimization',
+    long_description=long_description,
+    url='https://github.com/mirca/yacoub',
+    author='mirca',
+    author_email='jvmirca@gmail.com',
+    license='MIT',
+    classifiers=[
+        'Development Status :: 3 - Alpha',
+        'Intended Audience :: Science/Research',
+        'License :: OSI Approved :: MIT License',
+        'Programming Language :: Python :: 3.6',
+    ],
+    tests_require=['pytest', 'pytest-cov'],
+    keywords='statistics probability',
+    install_requires=['numpy', 'scipy']
+)

### 2018-03-04 yacoub/__init__.py

@@ -1,0 +1,2 @@
+from distributions import *
+from sampling import *

### 2018-03-07 yacoub/__init__.py
add stuff

@@ -1,2 +1,2 @@
-from distributions import *
-from sampling import *
+from .distributions import *
+from .sampling import *

### 2018-03-07 yacoub/distributions.py

@@ -36,7 +36,7 @@ class Distribution(ABC):
         size : int
             Size of the sample (number of realizations).
         """
-        return rejection_samples(self.pdf, x, size)
+        return rejection_sampling(self.pdf, x, size)
 
 
 class ComplexDistribution(Distribution):
@@ -60,8 +60,8 @@ class ComplexDistribution(Distribution):
         if len(x) != len(y):
             raise ValueError("x and y must have the same length.")
 
-        return (rejection_samples(self.pdf, x, size)
-                + 1j * rejection_samples(self.pdf, y, size))
+        return (rejection_sampling(self.pdf, x, size)
+                + 1j * rejection_sampling(self.pdf, y, size))
 
 
 class AlphaMu(Distribution):
@@ -186,5 +186,5 @@ class ComplexKappaMu(object):
                 / (2.0 * sigma2 * np.abs(q) ** (0.5 * self.mu - 1.0) * np.cosh(q * x / sigma2)))
 
     def rvs(self, x, y, size):
-        return (rejection_samples(self.real_part, x, y, size)
-                + 1j * rejection_samples(self.imag_part, x, y, size))
+        return (rejection_sampling(self.real_part, x, y, size)
+                + 1j * rejection_sampling(self.imag_part, x, y, size))

### 2018-03-07 paper/yacoub.tex
add stuff
push stuff

@@
 
-\author{\IEEEauthorblockN{Jos\'e~V.~de~M.~Cardoso,~Paulo~R.~Lins~Jr,~Wamberto~J.~L.~Queiroz,
+\author{\IEEEauthorblockN{Jos\'e~V.~de~M.~Cardoso,~Paulo~R.~Lins~Jr,
                           ~and~Marcelo~S.~Alencar,~\textit{IEEE Senior Member}}
 \IEEEauthorblockA{Universidade Federal de Campina Grande\\
+Instituto Federal de Educa\c c\~ao, Ciencia, e Tecnologia da Para\'iba
 Campina Grande, Para\'iba, Brazil\\
-\{josevinicius,paulo,wamberto,malencar\}@iecom.org.br\\}
+\{josevinicius,paulo,malencar\}@iecom.org.br\\}
 }
@@
     applicability of \texttt{yacoub} using examples in recent communications
-    system, namely: cooperative spectrum sensing, bit error rate computation
+    systems challenges, namely: cooperative spectrum sensing, bit error rate computation
     in generalized fading, and free space optics. The development of \texttt{yacoub}
@@
 \section{Examples}
-\subsection{Signal detection}
+\subsection{Signal detection and estimation}
 \subsection{Free Space Optics}
@@
 \bibliographystyle{IEEEtran}
-\bibliography{IEEEabrv,aps2016_regular.bib}
+\bibliography{IEEEabrv, yacoub.bib}
 

### 2018-03-07 setup.py

@@ -23,7 +23,7 @@ setup(
     name='yacoub',
     packages=['yacoub'],
     version='0.1.dev0',
-    description='A colorful, long-tailed package for beautiful Majorization-minimization',
+    description='Simulating fading channels in tensorflow',
     long_description=long_description,
     url='https://github.com/mirca/yacoub',
     author='mirca',
@@ -37,5 +37,5 @@ setup(
     ],
     tests_require=['pytest', 'pytest-cov'],
     keywords='statistics probability',
-    install_requires=['numpy', 'scipy']
+    install_requires=['numpy', 'scipy', 'tensorflow']
 )

### 2018-03-12 paper/yacoub.tex
add stuff

@@
 \usepackage{placeins}
+\usepackage{bm}
 %\usepackage{stfloats}
@@
 
-\author{\IEEEauthorblockN{Jos\'e~V.~de~M.~Cardoso,~Paulo~R.~Lins~Jr,
-                          ~and~Marcelo~S.~Alencar,~\textit{IEEE Senior Member}}
+\author{\IEEEauthorblockN{Jos\'e~V.~de~M.~Cardoso,~Paulo~R.~Lins~J\'unior,
+                          Wamberto~J.~L.~Queiroz,}
+        \IEEEauthorblockN{~Francisco~M.~Bernardino~J\'unior,~and~Marcelo~S.~Alencar,~\textit{IEEE Senior Member}}
 \IEEEauthorblockA{Universidade Federal de Campina Grande\\
-Instituto Federal de Educa\c c\~ao, Ciencia, e Tecnologia da Para\'iba
-Campina Grande, Para\'iba, Brazil\\
+Instituto Federal de Educa\c c\~ao, Ciencia, e Tecnologia da Para\'iba\\
+Campina Grande, Para\'iba, Brasil\\
+Universidade de Pernambuco\\
+Recife, Brasil\\
 \{josevinicius,paulo,malencar\}@iecom.org.br\\}
@@
     systems challenges, namely: cooperative spectrum sensing, bit error rate computation
-    in generalized fading, and free space optics. The development of \texttt{yacoub}
-    open source and its code is avaliable at \texttt{http://github.com/mirca/yacoub}.
+    in generalized fading channel, and parameter estimation in free space optics.
+    The development of \texttt{yacoub} open source and its code is avaliable at
+    \texttt{http://github.com/mirca/yacoub}.
 \end{abstract}
@@
 
+\subsection{Note on notation}
+Scalars and random variables are denoted as \textit{italic} small-case letters \textit{e.g.} $x$;
+vectors and random vectors are denoted as \textit{italic}, boldface, small-case letters \textit{e.g.} $\bm{x}$.
+A complex vector of length $n$ is defined as $\bm{x} \in \mathbb{C}^{1\times n}$. All
+vectors are column vectors. Matrices are denoted as \textit{italic}, boldface, capital
+letters as in $\bm{X}$; the identity matrix of order $n$ is denoted as $\bm{I}_n$.
+We define a discrete-time circularly symmetric Gaussian process $\bm{z}$ as any (finite or infinite) collection
+of random varibles $\bm{z}~=~\bm{x}~+~j\bm{y}$, $j \triangleq \sqrt{-1}$, such that
+$\bm{x}$ and $\bm{y}$ are iid jointly Gaussian with zero mean vector and covariance
+matrix given by $\mathbb{E}\left[\bm{z}\bm{z}^{\dagger}\right]$, in which $\bm{z}^\dagger$
+means the conjugate transpose of $\bm{z}$.
+
 \section{The Acceptance-Rejection sampler in log-space}
@@
 \section{Examples}
-\subsection{Signal detection and estimation}
-\subsection{Free Space Optics}
-\subsection{BER in $\alpha-\mu$ Fading}
+\subsection{Spectrum Sensing in Complex Generalized Fading Channels}
+
+The spectrum sensing problem consists in deciding whether or not a given channel
+frequency band is being occupied by a licensed (primary) user and, in case that such
+frequency band is available, how to opportuniscally allocate secondary users
+such that...
+
+From a probabilistic point of view, the spectrum sensing problem may be framed as
+a decision theory problem, as follows
+\begin{align}
+    \mathcal{H}_0:~& \bm{y} = \bm{w},\\
+    \mathcal{H}_1:~& \bm{y} = h\bm{s} + \bm{w},
+\end{align}
+in which $\bm{y} \in \mathbb{C}^{1\times n}$ is the decoded received vector,
+ $\bm{w} \in \mathbb{C}^{1\times n}$ is complex Gaussian noise process with
+ zero mean vector and covariance matrix given as $\sigma^2\bm{I}_n$
+
+\subsection{Parameter Estimation in Free Space Optics}
+
+\subsection{BER in Complex $\alpha-\mu$ Fading}
 

### 2018-03-13 paper/yacoub.tex
updates

@@
 \usepackage{bm}
+\usepackage{cite}
 %\usepackage{stfloats}
@@
 
-\author{\IEEEauthorblockN{Jos\'e~V.~de~M.~Cardoso,~Paulo~R.~Lins~J\'unior,
-                          Wamberto~J.~L.~Queiroz,}
-        \IEEEauthorblockN{~Francisco~M.~Bernardino~J\'unior,~and~Marcelo~S.~Alencar,~\textit{IEEE Senior Member}}
+\author{\IEEEauthorblockN{Jos\'e~V.~de~M.~Cardoso,~Paulo~R.~Lins~J\'unior,}
+        \IEEEauthorblockN{~Wamberto~J.~L.~Queiroz,~and~Marcelo~S.~Alencar,~\textit{IEEE Senior Member}}
 \IEEEauthorblockA{Universidade Federal de Campina Grande\\
@@
 Campina Grande, Para\'iba, Brasil\\
-Universidade de Pernambuco\\
-Recife, Brasil\\
-\{josevinicius,paulo,malencar\}@iecom.org.br\\}
+\{josevinicius,paulo,wamberto,malencar\}@iecom.org.br\\}
 }
@@
 vectors and random vectors are denoted as \textit{italic}, boldface, small-case letters \textit{e.g.} $\bm{x}$.
-A complex vector of length $n$ is defined as $\bm{x} \in \mathbb{C}^{1\times n}$. All
+The $n-$th component of a vector $\bm{x}$ is denoted as $x_n$.
+A complex vector of length $n$ is defined as $\bm{x} \in \mathbb{C}^{n\times 1}$. All
 vectors are column vectors. Matrices are denoted as \textit{italic}, boldface, capital
@@
 matrix given by $\mathbb{E}\left[\bm{z}\bm{z}^{\dagger}\right]$, in which $\bm{z}^\dagger$
-means the conjugate transpose of $\bm{z}$.
+means the conjugate transpose of $\bm{z}$ and $\mathbb{E}$ denotes the expected value. The
+probability of an event $A$ is denoted as $\mathbb{P}(A)$.
 
@@
 frequency band is available, how to opportuniscally allocate secondary users
-such that...
+such that the interference on the primary user is negligible.
 
@@
 \begin{align}
-    \mathcal{H}_0:~& \bm{y} = \bm{w},\\
-    \mathcal{H}_1:~& \bm{y} = h\bm{s} + \bm{w},
+    H_0:~& \bm{y} = \bm{w},\\
+    H_1:~& \bm{y} = h\bm{s} + \bm{w},
 \end{align}
-in which $\bm{y} \in \mathbb{C}^{1\times n}$ is the decoded received vector,
- $\bm{w} \in \mathbb{C}^{1\times n}$ is complex Gaussian noise process with
- zero mean vector and covariance matrix given as $\sigma^2\bm{I}_n$
+in which $\bm{y} \in \mathbb{C}^{n\times 1}$ is the decoded received vector signal,
+$\bm{w} \in \mathbb{C}^{n\times 1}$ is complex Gaussian noise process with zero mean
+vector and covariance matrix given as $\sigma^2\bm{I}_n$, and $h$ is the channel gain.
+
+In~\cite{cardoso2017}, the authors have shown that the probability distribution of the
+energy statistic $\tilde{y} \triangleq \bm{y}^{\dagger}\bm{y}$ conditioned on the knowledge of $h$,
+in case that $\bm{s}$ is an $M$-PSK signal such that every symbol has the same probability of occurrence,
+$\mathbb{P}(s_n = s) = \frac{1}{M}$, is given as
+\begin{align}
+    p(\tilde{y} | h, H_1) = 1 - Q_{n}\left(\sqrt{\dfrac{2n|h|^2E_s}{\sigma^2}}, \sqrt{\dfrac{2\tilde{y}}{\sigma^2}}\right),
+\end{align}
+in which $Q_{n}$ is the Marcum-$Q$ function and $E_s$ is the energy per symbol.
+
+The pdf of $\tilde{y}$ can be written using the Law of Total Expectation
+\begin{align}
+    p(\tilde{y} | H_1) = \mathbb{E}\left[p(\tilde{y} | h, H_{1})\right]
+                 = \int_{-\infty}^{+\infty} p(\tilde{y} | h, H_1)p(h)\;\mathrm{d}h.
+\end{align}
+
+Recall that the energy detection rule can be expressed as
+\begin{equation}
+    d_\delta (\tilde{y}) =
+\left\{
+    \begin{array}{ll}
+        1, & \tilde{y} \geq \delta,\\
+        0, & \tilde{y} < \delta,
+    \end{array}
+\right.
+\end{equation}
+in which $\delta$ is a strictly positive real number known as energy threshold,
+and $d_\delta (\tilde{y}) = j,~j \in \{0,1\}$ means that the detector has decided
+in favor of the hypothesis $H_j$.
+
+As a result, the probabilities of false alarm and detection can
+be written as
+\begin{align}
+    p_f = 1 - p()\\
+    p_d =
+\end{align}
 
@@
 The authors would like to thank the Federal University of Campina Grande (UFCG)
-and the Institute for Advanced Studies in Communications (Iecom).
+and the Institute for Advanced Studies in Communications (Iecom) for supporting
+this research.
 

### 2018-03-14 paper/yacoub.tex
working on majorization-minimization

@@
     applicability of \texttt{yacoub} using examples in recent communications
-    systems challenges, namely: cooperative spectrum sensing, bit error rate computation
-    in generalized fading channel, and parameter estimation in free space optics.
-    The development of \texttt{yacoub} open source and its code is avaliable at
+    systems challenges, namely: spectrum sensing, bit error rate computation,
+    and parameter estimation in generalized fading channels. For the latter,
+    a Majorization-Minimization algorithm is derived. The development of
+    \texttt{yacoub} open source and its code is avaliable at
     \texttt{http://github.com/mirca/yacoub}.
@@
 matrix given by $\mathbb{E}\left[\bm{z}\bm{z}^{\dagger}\right]$, in which $\bm{z}^\dagger$
-means the conjugate transpose of $\bm{z}$ and $\mathbb{E}$ denotes the expected value. The
-probability of an event $A$ is denoted as $\mathbb{P}(A)$.
+means the conjugate transpose of $\bm{z}$. The expectation value wrt a random variable $x$
+is denoted as $\mathbb{E}_x$. The probability of an event $A$ is denoted as $\mathbb{P}(A)$.
+The indicator function is denoted as $\mathbb{I}(\cdot)$ and it evaluates to $1$ if its
+argument is true and $0$ otherwise.
 
@@
 \begin{align}
-    p(\tilde{y} | H_1) = \mathbb{E}\left[p(\tilde{y} | h, H_{1})\right]
+    p(\tilde{y} | H_1) = \mathbb{E}_{h}\left[p(\tilde{y} | h, H_{1})\right]
                  = \int_{-\infty}^{+\infty} p(\tilde{y} | h, H_1)p(h)\;\mathrm{d}h.
@@
 \begin{equation}
-    d_\delta (\tilde{y}) =
-\left\{
-    \begin{array}{ll}
-        1, & \tilde{y} \geq \delta,\\
-        0, & \tilde{y} < \delta,
-    \end{array}
+    d_\delta (\tilde{y}) = \mathbb{I}(\tilde{y} > \delta)
 \right.
@@
 in which $\delta$ is a strictly positive real number known as energy threshold,
-and $d_\delta (\tilde{y}) = j,~j \in \{0,1\}$ means that the detector has decided
+and $d_\delta (\tilde{y}) = j,~j \in \{0,1\}$, means that the detector has decided
 in favor of the hypothesis $H_j$.
 
-As a result, the probabilities of false alarm and detection can
+As a result, the probabilities of false alarm and miss detection can
 be written as
 \begin{align}
-    p_f = 1 - p()\\
-    p_d =
+    p_f &\triangleq \mathbb{P}\left(d_\delta(\tilde{y}) = 1 | H_0\right) = 1 -  p(\delta | H_0),\label{eq:pf} \\
+    p_d &\triangleq \mathbb{P}\left(d_\delta(\tilde{y}) = 0 | H_1\right) = \mathbb{E}_{h}\left[p(\delta, h | H_1)\right],
+\label{eq:pd}
 \end{align}
 
-\subsection{Parameter Estimation in Free Space Optics}
+\subsection{Parameter Estimation in $\alpha$-$\mu$ fading}
+
+The $\alpha$-$\mu$ fading probability density is given as
+\begin{align}
+p(h) = \dfrac{\alpha \mu^\mu h^{\alpha\mu -1}}{\Gamma(\mu)}\exp\left(-\mu h^\alpha\right),
+\end{align}
+$h \in \mathbb{R}_{+}$, $\alpha \in \mathbb{R}_{+}$, and $\mu \in \mathbb{R}_{+}$.
+
+Given a vector $\bm{h} \in \mathbb{R}^{n \times 1}$ of iid samples from the
+$\alpha-\mu$ distribution, we would like to estimate the value of $\alpha$.
+The pdf of $\bm{h}$ is given as
+\begin{align}
+    p(\bm{h}) = \prod_{i=1}^{n}p(h_i) = \prod_{i=1}^{n}\dfrac{\alpha \mu^\mu h_i^{\alpha\mu -1}}
+    {\Gamma(\mu)}\exp\left(-\mu h_i^\alpha\right)\\
+    = \left(\dfrac{\alpha \mu^\mu }{\Gamma(\mu)}\right)^{n}
+    \exp\left(-\mu\sum_{i=1}^{n}h_i^{\alpha}\right)\prod_{i=1}^{n}h_i^{\alpha\mu -1}
+\end{align}
+and the log likelihood function (up to an additive constant that does not depend
+upon $\alpha$) is given as
+\begin{align}
+    \log p(\bm{h}) \cong n\log\alpha - \mu\sum_{i=1}^{n}h_i^{\alpha} + \alpha\mu\sum_{i=1}^{n}\log h_i
+\end{align}
+Noting that
+\begin{equation}
+    \sum_{i=1}^{n}h_i^{\alpha} \geq \sum_{i=1}^{n} h_i^{\alpha_t} + (\alpha - \alpha_t)\sum_{i=1}^{n}h_i^{\alpha_t}\log h_i
+\end{equation}
+and therefore
+\begin{align}
+    \log p(\bm{h}) \leq n\log\alpha - \mu\left(\sum_{i=1}^{n} h_i^{\alpha_t} +
+    (\alpha - \alpha_t)\sum_{i=1}^{n}h_i^{\alpha_t}\log h_i\right) + \alpha\mu\sum_{i=1}^{n}\log h_i
+\end{align}
 

### 2018-03-15 paper/yacoub.tex
add more maths

@@
     systems challenges, namely: spectrum sensing, bit error rate computation,
-    and parameter estimation in generalized fading channels. For the latter,
-    a Majorization-Minimization algorithm is derived. The development of
+    and parameter estimation in generalized fading channels. The development of
     \texttt{yacoub} open source and its code is avaliable at
@@
 letters as in $\bm{X}$; the identity matrix of order $n$ is denoted as $\bm{I}_n$.
-We define a discrete-time circularly symmetric Gaussian process $\bm{z}$ as any (finite or infinite) collection
+We define a discrete-time circularly symmetric Gaussian process $\bm{z}$ as any collection
 of random varibles $\bm{z}~=~\bm{x}~+~j\bm{y}$, $j \triangleq \sqrt{-1}$, such that
@@
 \section{The Acceptance-Rejection sampler in log-space}
+
+\section{Majorization-Minimization Algorithms}
 
@@
 
+\subsection{Parameter Estimation in Nakagami-$m$ fading}
+\begin{align}
+p(\bm{h}) = & \prod_{i=1}^{n}\dfrac{2m^m}{\Gamma(m)\Omega^{m}}h_i^{2m - 1}
+              \exp\left(-\dfrac{mh_i^2}{\Omega}\right) \\
+          = & \left(\dfrac{2m^m}{\Gamma(m)\Omega^{m}}\right)^{n}
+          \exp\left(-\dfrac{m\sum_{i=1}^{n}h_i^2}{\Omega}\right) \prod_{i=1}^{n}h_i^{2m - 1}
+\end{align}
+\begin{align}
+    \log p(\bm{h}) \cong &~n\left(m\left(\log m - \log\Omega\right) - \log\Gamma(m)\right)\nonumber
+    \\ & -m\left(\dfrac{\sum_{i=1}^{n}h_i^2}{\Omega} - 2\sum_{i=1}^{n}\log h_i\right)
+    \label{eq:loglike}
+\end{align}
+
+A direct maximum likelihood estimator for (\ref{eq:loglike}) has been investigated to be infeasible~\cite{paper}.
+
+Therefore, we use a Majorization-Minimization algorithm to find smooth
+and easy to optimize upper bounds for $\log p(\bm{h})$.
+
+Note that,
+\begin{align}
+    -\log\Gamma(m) \geq &-\log\Gamma(m_t) + (m - m_t) \nonumber \\
+                        &+ \left(m_t - \dfrac{1}{2}\right)\log (m_t-1)\nonumber\\
+                        &-\left(m - \dfrac{1}{2}\right)\log (m-1), m \geq m_t > 1
+\end{align}
+and
+\begin{align}
+    &m \log m \geq m\log m_t + m - m_t,~m > 0\\
+    & - m\log (m-1) \geq - \log(m-1) - (m-1)\left(\log (m_t-1) + \dfrac{m-1}{m_t-1} - 1\right),~m > 1
+\end{align}
+(in all inequalities, equality is achieved iff $m = m_t$).
+
+Therefore,
+\begin{figure*}[!htb]
+\begin{align}
+    - \log p(\bm{h}) \leq -n&\left(m\log m_t + 2(m - m_t) - m\log\Omega - \log\Gamma(m_t) +
+        \left(m_t - \dfrac{1}{2}\right)\log (m_t-1) - \dfrac{1}{2}\log(m-1)\right. \nonumber\\
+        &\left.-(m-1)\left(\log (m_t-1) + \dfrac{m-1}{m_t-1} - 1\right)
+        \right) +m\left(\dfrac{\sum_{i=1}^{n}h_i^2}{\Omega} - 2\sum_{i=1}^{n}\log h_i\right), m \geq m_t > 1.
+\end{align}
+\end{figure*}
+
+\begin{figure*}[!htb]
+    \begin{align}
+    \dfrac{\partial g(m | m_t)}{\partial m} = -n\left(\log m_t + 2 - \log\Omega - \dfrac{1}{2(m - 1)}
+    - \left(\log (m_t - 1) - 1\right) + \dfrac{-2m + 1}{m_t - 1} \right)
+    + \dfrac{\sum_{i=1}^{n}h_i^2}{\Omega} - 2\sum_{i=1}^{n}\log h_i = 0
+    \end{align}
+\end{figure*}
+
+\begin{figure*}[!htb]
+    \begin{align}
+        2(m - 1) \left(-n\left(\log m_t + 2 - \log\Omega - (\log(m_t - 1) - 1)\right) + \dfrac{\sum_{i=1}^{n}h_i^2}{\Omega} - 2\sum_{i=1}^{n}\log h_i \right) + n - \dfrac{2n}{m_t-1}(-2m^2 + 3m - 1) = 0\\
+        2(m - 1) a + n - \dfrac{2n}{m_t-1}(-2m^2 + 3m - 1) = 0\\
+        m^2\left(\dfrac{4n}{m_t - 1}\right) + m\left(\dfrac{6n}{m_t - 1} + 2a\right) -2a + n\left(\dfrac{m_t +1}{m_t - 1}\right) = 0\\
+    \end{align}
+\end{figure*}
+
 \subsection{Parameter Estimation in $\alpha$-$\mu$ fading}
@@
 Given a vector $\bm{h} \in \mathbb{R}^{n \times 1}$ of iid samples from the
-$\alpha-\mu$ distribution, we would like to estimate the value of $\alpha$.
+$\alpha-\mu$ distribution, we would like to estimate the value of...
 The pdf of $\bm{h}$ is given as
@@
 \end{align}
-and the log likelihood function (up to an additive constant that does not depend
-upon $\alpha$) is given as
+and the loglikelihood is given as
 \begin{align}
-    \log p(\bm{h}) \cong n\log\alpha - \mu\sum_{i=1}^{n}h_i^{\alpha} + \alpha\mu\sum_{i=1}^{n}\log h_i
+    \log p(\bm{h}) \cong
+    &~n\left(\log\alpha + \mu \log \mu - \log \Gamma(\mu)\right) \nonumber\\
+    & - \mu\sum_{i=1}^{n}h_i^{\alpha} + \alpha\mu\sum_{i=1}^{n}\log h_i
 \end{align}
-Noting that
-\begin{equation}
-    \sum_{i=1}^{n}h_i^{\alpha} \geq \sum_{i=1}^{n} h_i^{\alpha_t} + (\alpha - \alpha_t)\sum_{i=1}^{n}h_i^{\alpha_t}\log h_i
-\end{equation}
-and therefore
+
+Therefore, we want to solve
 \begin{align}
-    \log p(\bm{h}) \leq n\log\alpha - \mu\left(\sum_{i=1}^{n} h_i^{\alpha_t} +
-    (\alpha - \alpha_t)\sum_{i=1}^{n}h_i^{\alpha_t}\log h_i\right) + \alpha\mu\sum_{i=1}^{n}\log h_i
+    & \text{minimize} -\log p(\bm{h})\\
+    & \text{s.t.}~\alpha > 0, \bm{h} > 0 \nonumber
 \end{align}

### 2018-03-17 paper/yacoub.tex
update paper

@@
     systems challenges, namely: spectrum sensing, bit error rate computation,
-    and parameter estimation in generalized fading channels. The development of
-    \texttt{yacoub} open source and its code is avaliable at
-    \texttt{http://github.com/mirca/yacoub}.
+    and parameter estimation in generalized fading channels. For the latter,
+    we develop an iterative algorithm based on the Majorization-Minimization
+    framework. The development of \texttt{yacoub} is open source and its code
+    is avaliable at \texttt{http://github.com/mirca/yacoub}.
 \end{abstract}
@@
 is denoted as $\mathbb{E}_x$. The probability of an event $A$ is denoted as $\mathbb{P}(A)$.
-The indicator function is denoted as $\mathbb{I}(\cdot)$ and it evaluates to $1$ if its
-argument is true and $0$ otherwise.
+The indicator function is denoted as $\mathbb{I}(\cdot)$ and it evaluates to one if its
+argument is true and zero otherwise.
 
@@
 
-Note that,
+\textit{A parte problem\'atica aqui \'e encontrar um limitante inferior
+para a fun\c c\~ao Gamma. Talvez serie de Taylor resolva.}
+
+\subsection{BER in Complex $\alpha-\mu$ Fading}
+
+Consider the system
 \begin{align}
-    -\log\Gamma(m) \geq &-\log\Gamma(m_t) + (m - m_t) \nonumber \\
-                        &+ \left(m_t - \dfrac{1}{2}\right)\log (m_t-1)\nonumber\\
-                        &-\left(m - \dfrac{1}{2}\right)\log (m-1), m \geq m_t > 1
+    \bm{y} = h\bm{s} + \bm{w}
 \end{align}
-and
+in which $\bm{s} \in \mathbb{C}^{n\times 1}$ is a complex On-Off Keying (OOK) signal,
+$h$ is a complex $\alpha-\mu$ random variable and $\bm{w}$ is a complex Gaussian process
+with zero mean vector and covariance matrix equals $\sigma^2\bm{I}_n$, and $\bm{y}$ is
+the received complex vector signal.
+
+Assume that the OOK symbols are equiprobable and that there exist no interference
+between the in-phase and quadrature components, then the probability of one bit error
+is given as
 \begin{align}
-    &m \log m \geq m\log m_t + m - m_t,~m > 0\\
-    & - m\log (m-1) \geq - \log(m-1) - (m-1)\left(\log (m_t-1) + \dfrac{m-1}{m_t-1} - 1\right),~m > 1
-\end{align}
-(in all inequalities, equality is achieved iff $m = m_t$).
-
-Therefore,
-\begin{figure*}[!htb]
-\begin{align}
-    - \log p(\bm{h}) \leq -n&\left(m\log m_t + 2(m - m_t) - m\log\Omega - \log\Gamma(m_t) +
-        \left(m_t - \dfrac{1}{2}\right)\log (m_t-1) - \dfrac{1}{2}\log(m-1)\right. \nonumber\\
-        &\left.-(m-1)\left(\log (m_t-1) + \dfrac{m-1}{m_t-1} - 1\right)
-        \right) +m\left(\dfrac{\sum_{i=1}^{n}h_i^2}{\Omega} - 2\sum_{i=1}^{n}\log h_i\right), m \geq m_t > 1.
-\end{align}
-\end{figure*}
-
-\begin{figure*}[!htb]
-    \begin{align}
-    \dfrac{\partial g(m | m_t)}{\partial m} = -n\left(\log m_t + 2 - \log\Omega - \dfrac{1}{2(m - 1)}
-    - \left(\log (m_t - 1) - 1\right) + \dfrac{-2m + 1}{m_t - 1} \right)
-    + \dfrac{\sum_{i=1}^{n}h_i^2}{\Omega} - 2\sum_{i=1}^{n}\log h_i = 0
-    \end{align}
-\end{figure*}
-
-\begin{figure*}[!htb]
-    \begin{align}
-        2(m - 1) \left(-n\left(\log m_t + 2 - \log\Omega - (\log(m_t - 1) - 1)\right) + \dfrac{\sum_{i=1}^{n}h_i^2}{\Omega} - 2\sum_{i=1}^{n}\log h_i \right) + n - \dfrac{2n}{m_t-1}(-2m^2 + 3m - 1) = 0\\
-        2(m - 1) a + n - \dfrac{2n}{m_t-1}(-2m^2 + 3m - 1) = 0\\
-        m^2\left(\dfrac{4n}{m_t - 1}\right) + m\left(\dfrac{6n}{m_t - 1} + 2a\right) -2a + n\left(\dfrac{m_t +1}{m_t - 1}\right) = 0\\
-    \end{align}
-\end{figure*}
-
-\subsection{Parameter Estimation in $\alpha$-$\mu$ fading}
-
-The $\alpha$-$\mu$ fading probability density is given as
-\begin{align}
-p(h) = \dfrac{\alpha \mu^\mu h^{\alpha\mu -1}}{\Gamma(\mu)}\exp\left(-\mu h^\alpha\right),
-\end{align}
-$h \in \mathbb{R}_{+}$, $\alpha \in \mathbb{R}_{+}$, and $\mu \in \mathbb{R}_{+}$.
-
-Given a vector $\bm{h} \in \mathbb{R}^{n \times 1}$ of iid samples from the
-$\alpha-\mu$ distribution, we would like to estimate the value of...
-The pdf of $\bm{h}$ is given as
-\begin{align}
-    p(\bm{h}) = \prod_{i=1}^{n}p(h_i) = \prod_{i=1}^{n}\dfrac{\alpha \mu^\mu h_i^{\alpha\mu -1}}
-    {\Gamma(\mu)}\exp\left(-\mu h_i^\alpha\right)\\
-    = \left(\dfrac{\alpha \mu^\mu }{\Gamma(\mu)}\right)^{n}
-    \exp\left(-\mu\sum_{i=1}^{n}h_i^{\alpha}\right)\prod_{i=1}^{n}h_i^{\alpha\mu -1}
-\end{align}
-and the loglikelihood is given as
-\begin{align}
-    \log p(\bm{h}) \cong
-    &~n\left(\log\alpha + \mu \log \mu - \log \Gamma(\mu)\right) \nonumber\\
-    & - \mu\sum_{i=1}^{n}h_i^{\alpha} + \alpha\mu\sum_{i=1}^{n}\log h_i
+    p_{e} = \dfrac{1}{2}\left(\mathbb{P}\left(\hat{y}_i = 0 | s_{i} = 1\right)
+                            + \mathbb{P}\left(\hat{y}_i = 1 | s_{i} = 0\right)\right).
 \end{align}
 
-Therefore, we want to solve
-\begin{align}
-    & \text{minimize} -\log p(\bm{h})\\
-    & \text{s.t.}~\alpha > 0, \bm{h} > 0 \nonumber
-\end{align}
-
-\subsection{BER in Complex $\alpha-\mu$ Fading}
+Assume that the decoded vector $\bm{\hat{y}}$ is estimated using the minimum distance decoding
+rule, i.e.,
 

### 2018-03-17 paper/yacoub.tex
...

@@
 
-\subsection{Note on notation}
+\subsection*{Note on notation}
 Scalars and random variables are denoted as \textit{italic} small-case letters \textit{e.g.} $x$;
@@
 \textit{A parte problem\'atica aqui \'e encontrar um limitante inferior
-para a fun\c c\~ao Gamma. Talvez serie de Taylor resolva.}
+para a fun\c c\~ao Gamma. Talvez serie de Taylor resolva. Isto \'e, precisamos
+encontrar inequacoes da forma}
+
+\begin{align}
+    m\log m \geq \\
+    -\log \Gamma(m) \geq
+\end{align}
 

### 2018-03-18 paper/yacoub.tex
inequacao 24 de Sun and Palomar 2016 resolve
workz

--- 2018-03-17 paper/yacoub.tex
@@
     we develop an iterative algorithm based on the Majorization-Minimization
-    framework. The development of \texttt{yacoub} is open source and its code
+    framework, which allows reliable estimation of the fading parameter.
+    The development of \texttt{yacoub} is open source and its code
     is avaliable at \texttt{http://github.com/mirca/yacoub}.
@@
 
-\subsection{Note on notation}
-Scalars and random variables are denoted as \textit{italic} small-case letters \textit{e.g.} $x$;
+\subsection*{Note on notation}
+Scalars and random variables are denoted as \textit{italic}, small-case letters \textit{e.g.} $x$;
+sets and events are denoted as \textit{italic}, capital letters \textit{e.g.}, $A$;
 vectors and random vectors are denoted as \textit{italic}, boldface, small-case letters \textit{e.g.} $\bm{x}$.
@@
 We define a discrete-time circularly symmetric Gaussian process $\bm{z}$ as any collection
-of random varibles $\bm{z}~=~\bm{x}~+~j\bm{y}$, $j \triangleq \sqrt{-1}$, such that
-$\bm{x}$ and $\bm{y}$ are iid jointly Gaussian with zero mean vector and covariance
+of random variables $\bm{z}~=~\bm{x}~+~j\bm{y}$, $j \triangleq \sqrt{-1}$, such that
+$\bm{x}$ and $\bm{y}$ are i.i.d. jointly Gaussian, with zero mean vector and covariance
 matrix given by $\mathbb{E}\left[\bm{z}\bm{z}^{\dagger}\right]$, in which $\bm{z}^\dagger$
-means the conjugate transpose of $\bm{z}$. The expectation value wrt a random variable $x$
-is denoted as $\mathbb{E}_x$. The probability of an event $A$ is denoted as $\mathbb{P}(A)$.
-The indicator function is denoted as $\mathbb{I}(\cdot)$ and it evaluates to one if its
-argument is true and zero otherwise.
+means the conjugate transpose of $\bm{z}$. The expectation value w.r.t. to the porbability
+distribution of a random variable $x$ is denoted as $\mathbb{E}_x$. The probability of an
+event $A$ is denoted as $\mathbb{P}(A)$. The indicator function is denoted as $\mathbb{I}(\cdot)$,
+it evaluates to one if its argument is true and zero otherwise. For any given two real functions $f$ and $g$
+defined on the same domain $D$, $f \cong g$ means that there exist a constant $c$ such that
+$f(\bm{x}) = g(\bm{x}) + c$, $\forall~ \bm{x} \in D$.
 
@@
 \subsection{Parameter Estimation in Nakagami-$m$ fading}
+The Nakagami-$m$ density is given as
 \begin{align}
-p(\bm{h}) = & \prod_{i=1}^{n}\dfrac{2m^m}{\Gamma(m)\Omega^{m}}h_i^{2m - 1}
-              \exp\left(-\dfrac{mh_i^2}{\Omega}\right) \\
+    p(\bm{h})& = \prod_{i=1}^{n}\dfrac{2m^m}{\Gamma(m)\Omega^{m}}h_i^{2m - 1}
+              \exp\left(-\dfrac{mh_i^2}{\Omega}\right) \nonumber \\
           = & \left(\dfrac{2m^m}{\Gamma(m)\Omega^{m}}\right)^{n}
@@
 \end{align}
+And the log likelihood function (up to an additive constant) is given as
 \begin{align}
@@
 
-A direct maximum likelihood estimator for (\ref{eq:loglike}) has been investigated to be infeasible~\cite{paper}.
+A direct maximum likelihood estimator for (\ref{eq:loglike}) has been
+investigated to be infeasible~\cite{paper}.
 
 Therefore, we use a Majorization-Minimization algorithm to find smooth
-and easy to optimize upper bounds for $\log p(\bm{h})$.
+and easy to optimize upper bounds for $\log p(\bm{h})$. More precisely,
+we need to find lower bounds for $m\log m$ and $-\log \Gamma(m)$ for $m \geq \frac{1}{2}$.
+The former function is convex for $m \geq \frac{1}{2}$, hence it can be lower bounded
+by its first order Taylor series as
+\begin{align}
+    m \log m \geq m(1 + \log m_t) - m_t,
+    \label{eq:lower-bound-mlogm}
+\end{align}
+equality is achived at $m = m_t$. The function $-\log \Gamma(m)$, on the other hand,
+is concave nonetheless it can be lower bounded by its second order Taylor series expansion
+as
+\begin{align}
+    -\log \Gamma(m) \geq& - \log \Gamma(m_t) - \psi(m_t) (m - m_t)\nonumber\\
+                        & - \frac{\psi'\left(\frac{1}{2}\right)}{2}(m - m_t) ^ 2,
+                        ~m \geq \frac{1}{2},~m_t \geq \frac{1}{2}
+    \label{eq:lower-bound-negloggamma}
+\end{align}
+in which $\psi(x) = \dfrac{\Gamma'(x)}{\Gamma(x)}$ is known as the digamma function;
+equality is achieved at $m = m_t$.
 
-\textit{A parte problem\'atica aqui \'e encontrar um limitante inferior
-para a fun\c c\~ao Gamma. Talvez serie de Taylor resolva.}
+Substituting (\ref{eq:lower-bound-mlogm}) and (\ref{eq:lower-bound-negloggamma}) into
+(\ref{eq:loglike}), a valid lower bound for $\log p(\bm{h})$ is obtained in~(\ref{eq:surrogate}).
+Due to the simple form of $g(m | m_t)$, its maximizer can be found in closed form, and
+an updating rule for the MLE can be written as
+\begin{align}
+    m_{t+1} = \dfrac{1}{\psi'(\frac{1}{2})}&\left(1 + \log \frac{m_t}{\Omega} - \psi(m_t)\right.\nonumber\\
+    &+ \left.\dfrac{1}{n} \left(2\sum_{i=1}^{n}\log h_i - \frac{\sum_{i=1}^{n}h_i^2}{\Omega}\right)\right)
+\end{align}
+
+\begin{figure*}[!htb]
+\begin{align}
+    g(m | m_t) = n\left(-m\log\Omega  + m(1 + \log m_t) - m_t
+    -\log \Gamma(m_t) - \psi(m_t) (m - m_t) - \frac{\psi'\left(\frac{1}{2}\right)}{2}(m - m_t)^2\right)
+    -m\left(\dfrac{\sum_{i=1}^{n}h_i^2}{\Omega} - 2\sum_{i=1}^{n}\log h_i\right)
+    \label{eq:surrogate}
+\end{align}
+\end{figure*}
 

### 2018-03-18 yacoub/sampling.py
use the acceptance rejection in linear space for now

@@ -34,8 +34,8 @@ def rejection_sampling(pdf, x, n_samples, *args):
 
     while len(accepted_samples) < n_samples:
         unif_x = np.random.uniform(low=x_min, high=x_max, size=n_samples)
-        unif_y = np.random.uniform(low=pdf_min, high=1., size=n_samples)
-        accept = np.log(unif_y) <= (np.log(pdf(unif_x, *args)) - math.log(pdf_max))
+        unif_y = np.random.uniform(low=pdf_min, high=pdf_max, size=n_samples)
+        accept = unif_y <= pdf(unif_x, *args)
         accepted_samples = np.concatenate([accepted_samples, unif_x[accept]])
 
     return accepted_samples[:n_samples]

### 2018-03-21 paper/yacoub.tex
updates

@@
     generalized fading channels, named \texttt{yacoub}. We describe the
-    applicability of \texttt{yacoub} using examples in recent communications
-    systems challenges, namely: spectrum sensing, bit error rate computation,
-    and parameter estimation in generalized fading channels. For the latter,
-    we develop an iterative algorithm based on the Majorization-Minimization
-    framework, which allows reliable estimation of the fading parameter.
-    The development of \texttt{yacoub} is open source and its code
-    is avaliable at \texttt{http://github.com/mirca/yacoub}.
+    applicability of \texttt{yacoub} using examples in scenarios of communications
+    channels impaired by generalized fading, namely: spectrum sensing, bit error
+    rate computation, and fading estimation. For the latter, we develop an iterative
+    algorithm using the Majorization-Minimization framework, which allows reliable
+    estimation of the fading parameter. The development of \texttt{yacoub} is open
+    source and its code along with examples are avaliable at
+    \texttt{http://github.com/mirca/yacoub}.
 \end{abstract}
@@
 
-\subsection*{Note on notation}
-Scalars and random variables are denoted as \textit{italic}, small-case letters \textit{e.g.} $x$;
-sets and events are denoted as \textit{italic}, capital letters \textit{e.g.}, $A$;
-vectors and random vectors are denoted as \textit{italic}, boldface, small-case letters \textit{e.g.} $\bm{x}$.
-The $n-$th component of a vector $\bm{x}$ is denoted as $x_n$.
-A complex vector of length $n$ is defined as $\bm{x} \in \mathbb{C}^{n\times 1}$. All
-vectors are column vectors. Matrices are denoted as \textit{italic}, boldface, capital
-letters as in $\bm{X}$; the identity matrix of order $n$ is denoted as $\bm{I}_n$.
-We define a discrete-time circularly symmetric Gaussian process $\bm{z}$ as any collection
-of random variables $\bm{z}~=~\bm{x}~+~j\bm{y}$, $j \triangleq \sqrt{-1}$, such that
-$\bm{x}$ and $\bm{y}$ are i.i.d. jointly Gaussian, with zero mean vector and covariance
-matrix given by $\mathbb{E}\left[\bm{z}\bm{z}^{\dagger}\right]$, in which $\bm{z}^\dagger$
-means the conjugate transpose of $\bm{z}$. The expectation value w.r.t. to the porbability
-distribution of a random variable $x$ is denoted as $\mathbb{E}_x$. The probability of an
-event $A$ is denoted as $\mathbb{P}(A)$. The indicator function is denoted as $\mathbb{I}(\cdot)$,
-it evaluates to one if its argument is true and zero otherwise. For any given two real functions $f$ and $g$
-defined on the same domain $D$, $f \cong g$ means that there exist a constant $c$ such that
+\subsection*{Notation}
+Scalars and random variables are denoted as \textit{italic}, small-case letters
+\textit{e.g.} $x$; sets and events are denoted as \textit{italic}, capital
+letters \textit{e.g.}, $A$; vectors and random vectors are denoted as
+\textit{italic}, boldface, small-case letters \textit{e.g.} $\bm{x}$. The $n-$th
+component of a vector $\bm{x}$ is denoted as $x_n$. A complex vector of length
+$n$ is defined as $\bm{x} \in \mathbb{C}^{n\times 1}$. All vectors are column
+vectors. Matrices are denoted as \textit{italic}, boldface, capital letters as
+in $\bm{X}$; the identity matrix of order $n$ is denoted as $\bm{I}_n$. We
+define a discrete-time circularly symmetric Gaussian process $\bm{z}$ as any
+collection of random variables $\bm{z}~=~\bm{x}~+~j\bm{y}$,
+$j \triangleq \sqrt{-1}$, such that $\bm{x}$ and $\bm{y}$ are i.i.d. jointly
+Gaussian, with zero mean vector and covariance matrix given by
+$\mathbb{E}\left[\bm{z}\bm{z}^{\dagger}\right]$, in which $\bm{z}^\dagger$ means
+the conjugate transpose of $\bm{z}$. The expectation value w.r.t. to the
+probability distribution of a random variable $x$ is denoted as $\mathbb{E}_x$.
+The probability of an event $A$ is denoted as $\mathbb{P}(A)$. The indicator
+function is denoted as $\mathbb{I}(\cdot)$, it evaluates to one if its argument
+is true and zero otherwise. For any given two real functions $f$ and $g$ defined
+on the same domain $D$, $f \cong g$ means that there exist a constant $c$ such that
 $f(\bm{x}) = g(\bm{x}) + c$, $\forall~ \bm{x} \in D$.
@@
 
-A direct maximum likelihood estimator for (\ref{eq:loglike}) has been
+A direct maximum likelihood estimator (MLE) for (\ref{eq:loglike}) has been
 investigated to be infeasible~\cite{paper}.
@@
 Therefore, we use a Majorization-Minimization algorithm to find smooth
-and easy to optimize upper bounds for $\log p(\bm{h})$. More precisely,
+and easy to optimize lower bounds for $\log p(\bm{h})$. More precisely,
 we need to find lower bounds for $m\log m$ and $-\log \Gamma(m)$ for $m \geq \frac{1}{2}$.
-The former function is convex for $m \geq \frac{1}{2}$, hence it can be lower bounded
+The former function is convex for $m \geq 0$, hence it can be lower bounded
 by its first order Taylor series as
@@
 \end{align}
-equality is achived at $m = m_t$. The function $-\log \Gamma(m)$, on the other hand,
-is concave nonetheless it can be lower bounded by its second order Taylor series expansion
-as
+The function $-\log \Gamma(m)$ is concave, therefore, it can be lower bounded
+by its second order Taylor series expansion as
 \begin{align}
@@
                         & - \frac{\psi'\left(\frac{1}{2}\right)}{2}(m - m_t) ^ 2,
-                        ~m \geq \frac{1}{2},~m_t \geq \frac{1}{2}
+                        ~m \geq \frac{1}{2},~m_t \geq \frac{1}{2},
     \label{eq:lower-bound-negloggamma}
 \end{align}
-in which $\psi(x) = \dfrac{\Gamma'(x)}{\Gamma(x)}$ is known as the digamma function;
-equality is achieved at $m = m_t$.
+in which $\psi(x) = \dfrac{\Gamma'(x)}{\Gamma(x)}$ is known as the digamma function.
+For both inequalities presented above, equality is achieved at $m = m_t$.
 
 Substituting (\ref{eq:lower-bound-mlogm}) and (\ref{eq:lower-bound-negloggamma}) into
-(\ref{eq:loglike}), a valid lower bound for $\log p(\bm{h})$ is obtained in~(\ref{eq:surrogate}).
+(\ref{eq:loglike}), a lower bound for $\log p(\bm{h})$ is obtained in~(\ref{eq:surrogate}).
 Due to the simple form of $g(m | m_t)$, its maximizer can be found in closed form, and
@@
 \begin{align}
-    m_{t+1} = \dfrac{1}{\psi'(\frac{1}{2})}&\left(1 + \log \frac{m_t}{\Omega} - \psi(m_t)\right.\nonumber\\
+    m_{t+1} = 1 + \dfrac{1}{\psi'(\frac{1}{2})}&\left(1 + \log \frac{m_t}{\Omega} - \psi(m_t)
+    + \right.\nonumber\\
     &+ \left.\dfrac{1}{n} \left(2\sum_{i=1}^{n}\log h_i - \frac{\sum_{i=1}^{n}h_i^2}{\Omega}\right)\right)
+\end{align}
+
+Additionally,
+note that $m_{t+1}$ is an estimator of the true parameter value $m$. Its expected value,
+conditioned on the knowledge of $m_t$, is given as
+\begin{align}
+    \mathbb{E}(m_{t+1} | m_t) = 1 + \dfrac{1}{\psi'(\frac{1}{2})}&\left(1 + \log \frac{m_t}{\Omega} - \psi(m_t)
+    + \right.\nonumber\\
+&+ \left.\dfrac{1}{n} \left(2\sum_{i=1}^{n}\mathbb{E}(\log h_i)
+- \frac{\sum_{i=1}^{n}\mathbb{E}\left(h_i^2\right)}{\Omega}\right)\right)
 \end{align}

### 2018-03-22 paper/yacoub.tex
changes

@@
 \begin{document}
-\title{\texttt{yacoub}: a Python package for Simulating Generalized Fading Channels}
+\title{\texttt{mady}: a Python package for Simulating Generalized Fading Channels}
 
-\author{\IEEEauthorblockN{Jos\'e~V.~de~M.~Cardoso,~Paulo~R.~Lins~J\'unior,}
-        \IEEEauthorblockN{~Wamberto~J.~L.~Queiroz,~and~Marcelo~S.~Alencar,~\textit{IEEE Senior Member}}
+\author{\IEEEauthorblockN{Jos\'e~V.~de~M.~Cardoso,~Wamberto~J.~L.~Queiroz,}
+        \IEEEauthorblockN{~Paulo~R.~Lins~J\'unior,~and~Marcelo~S.~Alencar,~\textit{IEEE Senior Member}}
 \IEEEauthorblockA{Universidade Federal de Campina Grande\\
@@
     We present a well tested Python-based library for simulating and computing
-    generalized fading channels, named \texttt{yacoub}. We describe the
-    applicability of \texttt{yacoub} using examples in scenarios of communications
+    generalized fading channels, named \texttt{mady}. We describe the
+    applicability of \texttt{mady} using examples in scenarios of communications
     channels impaired by generalized fading, namely: spectrum sensing, bit error
@@
     algorithm using the Majorization-Minimization framework, which allows reliable
-    estimation of the fading parameter. The development of \texttt{yacoub} is open
+    estimation of the fading parameter. The development of \texttt{mady} is open
     source and its code along with examples are avaliable at
-    \texttt{http://github.com/mirca/yacoub}.
+    \texttt{http://github.com/mirca/mady}.
 \end{abstract}
@@
 \bibliographystyle{IEEEtran}
-\bibliography{IEEEabrv, yacoub.bib}
+\bibliography{IEEEabrv, mady.bib}
 

### 2018-03-23 paper/manuscript.tex
updates

@@
-\documentclass{sbrt2013port}
-%\usepackage[brazil]{babel}
-\usepackage{amsmath}
+\documentclass[conference, 10pt]{IEEEtran}
+\usepackage[cmex10]{amsmath}
 \usepackage{amssymb}
@@
 \usepackage{color}
-%\usepackage{placeins}
+\usepackage{placeins}
 \usepackage{bm}
-%\usepackage{cite}
+\usepackage{cite}
 %\usepackage{stfloats}
-%\usepackage{float}
+\usepackage{float}
 \usepackage{hyperref}
-%\usepackage{cite}
+\usepackage{cite}
 \usepackage{tabularx,colortbl}
@@
 \begin{document}
+\title{\texttt{maoud}: a Python package for Simulating Generalized Fading Channels}
 
-\title{Simulating Generalized Fading Channels in Python}
-
-\author{José Vinícius de M. Cardoso$^1$,   Paulo Ribeiro Lins Júnior$^2$, Wamberto Queiroz$^1$ e Marcelo Sampaio de Alencar$^3$
-\thanks{\noindent Instituto de Estudos Avançados em Comunicações -- Iecom; $^1$Universidade Federal de Campina Grande -- UFCG; $^2$Grupo de Pesquisa em Comunicações e Processamento de Informação -- GComPI/Instituto Federal de Educação, Ciência e Tecnologia da Paraíba -- IFPB, Campus Campina Grande -- PB, $^3$Universidade Federal da Bahia -- UFBA, emails: $^1$\{josevinicius, wamberto\}@iecom.org.br, $^2$paulo.lins@ifpb.edu.br e $^3$malencar@iecom.org.br.}}
+\author{\IEEEauthorblockN{Jos\'e~V.~de~M.~Cardoso,~Wamberto~J.~L.~Queiroz,}
+        \IEEEauthorblockN{~Paulo~R.~Lins~J\'unior,~and~Marcelo~S.~Alencar,~\textit{IEEE Senior Member}}
+\IEEEauthorblockA{Universidade Federal de Campina Grande\\
+Instituto Federal de Educa\c c\~ao, Ciencia, e Tecnologia da Para\'iba\\
+Campina Grande, Para\'iba, Brasil\\
+\{josevinicius,paulo,wamberto,malencar\}@iecom.org.br\\}
+}
 
@@
 
-\markboth{XXXVI SIMPÓSIO BRASILEIRO DE TELECOMUNICAÇÕES E PROCESSAMENTO DE SINAIS - SBrT'2018, 16-19 DE SETEMBRO DE 2018, CAMPINA GRANDE, PB} {XXXVI SIMPÓSIO BRASILEIRO DE TELECOMUNICAÇÕES E PROCESSAMENTO DE SINAIS - SBrT'2018, 16-19 DE SETEMBRO DE 2018, CAMPINA GRANDE, PB}
-
 \begin{abstract}
-    We present a novel and well tested Python-based library for simulating and computing
-    generalized fading channels, considering $\alpha\text{-}\mu$, $\kappa\text{-}\mu$, and
-$\eta\text{-}\mu$ distributions. We describe the
-    applicability of this library using a few communications channels scenarios
-    impaired by generalized fading, namely, spectrum sensing and bit error
-    rate computation. The development of the library is open source and its code, along
-    with examples, are available at
+    We present a well tested Python-based library for simulating and computing
+    generalized fading channels, named \texttt{maoud}. We describe the
+    applicability of \texttt{maoud} using examples in scenarios of communications
+    channels impaired by generalized fading, namely: spectrum sensing, bit error
+    rate computation, and fading estimation. For the latter, we develop an iterative
+    algorithm using the Majorization-Minimization framework, which allows reliable
+    estimation of the fading parameter. The development of \texttt{maoud} is open
+    source and its code along with examples are avaliable at
     \texttt{http://github.com/mirca/maoud}.
@@
 
-\begin{keywords}
-Generalized Fading, Simulation, Python
-\end{keywords}
-
+\IEEEpeerreviewmaketitle
 \section{Introduction}
 
-The study of modern wireless communications systems heavily relies on fading channel simulation.
-By fading channel simulation, we refer to the generation of samples from a probability distribution
-that resembles the effects and impairments caused by real communications fading channels on the
-transmitted signal.
+\subsection*{Notation}
+Scalars and random variables are denoted as \textit{italic}, small-case letters
+\textit{e.g.} $x$; sets and events are denoted as \textit{italic}, capital
+letters \textit{e.g.}, $A$; vectors and random vectors are denoted as
+\textit{italic}, boldface, small-case letters \textit{e.g.} $\bm{x}$. The $n-$th
+component of a vector $\bm{x}$ is denoted as $x_n$. A complex vector of length
+$n$ is defined as $\bm{x} \in \mathbb{C}^{n\times 1}$. All vectors are column
+vectors. Matrices are denoted as \textit{italic}, boldface, capital letters as
+in $\bm{X}$; the identity matrix of order $n$ is denoted as $\bm{I}_n$. We
+define a discrete-time circularly symmetric Gaussian process $\bm{z}$ as any
+collection of random variables $\bm{z}~=~\bm{x}~+~j\bm{y}$,
+$j \triangleq \sqrt{-1}$, such that $\bm{x}$ and $\bm{y}$ are i.i.d. jointly
+Gaussian, with zero mean vector and covariance matrix given by
+$\mathbb{E}\left[\bm{z}\bm{z}^{\dagger}\right]$, in which $\bm{z}^\dagger$ means
+the conjugate transpose of $\bm{z}$. The expectation value w.r.t. to the
+probability distribution of a random variable $x$ is denoted as $\mathbb{E}_x$.
+The probability of an event $A$ is denoted as $\mathbb{P}(A)$. The indicator
+function is denoted as $\mathbb{I}(\cdot)$, it evaluates to one if its argument
+is true and zero otherwise. For any given two real functions $f$ and $g$ defined
+on the same domain $D$, $f \cong g$ means that there exist a constant $c$ such that
+$f(\bm{x}) = g(\bm{x}) + c$, $\forall~ \bm{x} \in D$.
 
-Although accurate and precise distributions for generalized fading have been
-estabilished in the literature, such as $\alpha\text{-}\mu$~\cite{yacoub.2007.1},
-$\kappa\text{-}\mu$~\cite{yacoub.2007.2} and $\eta\text{-}\mu$~\cite{yacoub.2007.2},
-the generation of samples following these distributions is usually
-a time-consuming task.
+\section{The Acceptance-Rejection sampler in log-space}
 
-In~\cite{cogliatti2012}, the authors built an efficient
-algorithm, based on the rejection method, for generation of samples from those
-distributions. However, there are neither open nor
-closed source implementations available to the scientific community.
+\section{Majorization-Minimization Algorithms}
 
-In this paper, we present an open source Python package
-for generation of samples following the $\alpha\text{-}\mu$, $\kappa\text{-}\mu$, and
-$\eta\text{-}\mu$ distributions. The usefullness of ths package is illustrated
-through well known examples involving spectrum sensing and bit error rate (BER) computation.
-
-\section{Rejection Sampling}\label{rejec}
-
-The algorithm implemented in this work, originally proposed in~\cite{cogliatti2012},
-is based on the rejection method, which is one of the most used for the generation
-of samples of a probability distribution.
-
-We briefly describe the algorithm as follows. Consider that we would like to simulate a
-random variable $x$ with a probability density $f$. The basic idea is to find
-an alternative probability density $g$, from which there exists an efficient procedure
-to generate samples, e.g., inverse methods. Additionally, it is required that $g$
-majorizes $f$, i.e., we assume that there exists a real number $c$ such that $f(x)/g(x) < c$.
-
-Basically, the steps of the rejection algorithm are~\cite{ross}:
-\begin{enumerate}
-	\item generate a sample $y$ from the probability density $g$;
-    \item generate a sample $u$ from a uniform density with support $(0, 1)$;
-	\item check $u \leq \frac{f(y)}{cg(y)}$; if true then accept $y$; otherwise, return to step 1.
-\end{enumerate}
-
-The implementation of this algorithm along with the code to efficiently generate
-samples from the $\alpha$-$\mu$, $\eta$-$\mu$, and $\kappa$-$\mu$ distributions
-is available at \url{http://github.com/mirca/maoud}.
-
-In order to validate the implementation, we apply the routines to
-two use cases in wireless communications: spectrum sensing and bit error rate computation.
-
-\section{Spectrum Sensing in Complex Generalized Fading Channels}~\label{sensing}
+\section{Examples}
+\subsection{Spectrum Sensing in Complex Generalized Fading Channels}
 
@@
 \begin{align}
-    H_0:  \bm{y} &= \bm{w},\\
-    H_1:  \bm{y} &= h\bm{s} + \bm{w},
+    H_0:~& \bm{y} = \bm{w},\\
+    H_1:~& \bm{y} = h\bm{s} + \bm{w},
 \end{align}
-\noindent in which $\bm{y} \in \mathbb{C}^{n\times 1}$ is the received vector signal,
+in which $\bm{y} \in \mathbb{C}^{n\times 1}$ is the decoded received vector signal,
 $\bm{w} \in \mathbb{C}^{n\times 1}$ is complex Gaussian noise process with zero mean
@@
 
-In~\cite{cardoso2017}, the authors have shown that the cumulative distribution function (cdf) of the
+In~\cite{cardoso2017}, the authors have shown that the probability distribution of the
 energy statistic $\tilde{y} \triangleq \bm{y}^{\dagger}\bm{y}$ conditioned on the knowledge of $h$,
@@
 \begin{align}
-    P(\tilde{y} | h, H_1) = 1 - \mathrm{Q}_{n}\left(\sqrt{\dfrac{2n|h|^2E_s}{\sigma^2}}, \sqrt{\dfrac{2\tilde{y}}{\sigma^2}}\right),
+    p(\tilde{y} | h, H_1) = 1 - Q_{n}\left(\sqrt{\dfrac{2n|h|^2E_s}{\sigma^2}}, \sqrt{\dfrac{2\tilde{y}}{\sigma^2}}\right),
 \end{align}
-in which $\mathrm{Q}_{n}$ is the Marcum-$\mathrm{Q}$ function and $E_s$ is the energy per symbol.
+in which $Q_{n}$ is the Marcum-$Q$ function and $E_s$ is the energy per symbol.
+
+The pdf of $\tilde{y}$ can be written using the Law of Total Expectation
+\begin{align}
+    p(\tilde{y} | H_1) = \mathbb{E}_{h}\left[p(\tilde{y} | h, H_{1})\right]
+                 = \int_{-\infty}^{+\infty} p(\tilde{y} | h, H_1)p(h)\;\mathrm{d}h.
+\end{align}
 
@@
     d_\delta (\tilde{y}) = \mathbb{I}(\tilde{y} > \delta)
+\right.
 \end{equation}
-in which $\mathbb{I}$ is the indicator function, $\delta$ is a strictly positive real
-number known as energy threshold, and $d_\delta (\tilde{y}) = j,~j \in \{0,1\}$,
-means that the detector has decided in favor of the hypothesis $H_j$.
+in which $\delta$ is a strictly positive real number known as energy threshold,
+and $d_\delta (\tilde{y}) = j,~j \in \{0,1\}$, means that the detector has decided
+in favor of the hypothesis $H_j$.
 
@@
 \begin{align}
-    \mathbb{P}\left(d_\delta(\tilde{y}) = 1 | H_0\right) &=
-        1 -  P(\delta | H_0) = 1 - \gamma\left(n, \frac{\delta}{\sigma^2}\right),\label{eq:pf} \\
-    \mathbb{P}\left(d_\delta(\tilde{y}) = 0 | H_1\right) & = \int_{-\infty}^{+\infty} P(\delta | h, H_1)p(h)\;\mathrm{d}h,\label{eq:pd}
+    p_f &\triangleq \mathbb{P}\left(d_\delta(\tilde{y}) = 1 | H_0\right) = 1 -  p(\delta | H_0),\label{eq:pf} \\
+    p_d &\triangleq \mathbb{P}\left(d_\delta(\tilde{y}) = 0 | H_1\right) = \mathbb{E}_{h}\left[p(\delta, h | H_1)\right],
+\label{eq:pd}
 \end{align}
-in which $\gamma$ is the regularized lower incomplete Gamma function, $p(h)$ is the pdf of the fading,
-and $\delta$ is the energy detection threshold.
 
-The performance of detection schemes can be measured by computing the Receiver Operating
-Characteristic (ROC), which consists in varying $\delta$ and computing the pairs of
-probability of false alarm and miss detection, as illustrated in Fig.~\ref{fig:spectrum-sensing}, in which the solid curve represents the theorectical probabilities as stated on
-(\ref{eq:pf}) and (\ref{eq:pd}) for different values of
-$\delta$, whereas bullets represent Monte Carlo simulations acquired with $10^6$ realizations.
-The input signal $\bm{s}$ consists in a vector of length $n=25$ in which each entry represents
-a symbol of a 64-PSK constellation. Symbols are assumed to be equiprobable and
-the signal-to-noise ratio is set to $5$ dB.
+\subsection{Parameter Estimation in Nakagami-$m$ fading}
+The Nakagami-$m$ density is given as
+\begin{align}
+    p(\bm{h})& = \prod_{i=1}^{n}\dfrac{2m^m}{\Gamma(m)\Omega^{m}}h_i^{2m - 1}
+              \exp\left(-\dfrac{mh_i^2}{\Omega}\right) \nonumber \\
+          = & \left(\dfrac{2m^m}{\Gamma(m)\Omega^{m}}\right)^{n}
+          \exp\left(-\dfrac{m\sum_{i=1}^{n}h_i^2}{\Omega}\right) \prod_{i=1}^{n}h_i^{2m - 1}
+\end{align}
+And the log likelihood function (up to an additive constant) is given as
+\begin{align}
+\log p(\bm{h}) \cong &~n\left(m\left(\log m - \log\Omega\right) - \log\Gamma(m)\right)\nonumber
+    \\ & -m\left(\dfrac{\sum_{i=1}^{n}h_i^2}{\Omega} - 2\sum_{i=1}^{n}\log h_i\right)
+    \label{eq:loglike}
+\end{align}
 
-\begin{figure}[!htb]
-    \centering
-    \includegraphics{figures/spectrum_sensing}
-    \caption{Receiver Operating Characteristic for the energy detector in $\alpha$-$\mu$
-             channel with $\alpha=2$ and $\mu=1$.
-             }
-    \label{fig:spectrum-sensing}
-\end{figure}
+A direct maximum likelihood estimator (MLE) for (\ref{eq:loglike}) has been
+investigated to be infeasible~\cite{cheng2001}.
 
-\section{Bit Error Rate in $\alpha$-$\mu$ Fading}~\label{ber}
+Therefore, we use a Majorization-Minimization algorithm to find smooth
+and easy to optimize lower bounds for $\log p(\bm{h})$. More precisely,
+we need to find lower bounds for $m\log m$ and $-\log \Gamma(m)$ for $m \geq \frac{1}{2}$.
+The former function is convex for $m \geq 0$, hence it can be lower bounded
+by its first order Taylor series as
+\begin{align}
+    m \log m \geq m(1 + \log m_t) - m_t,
+    \label{eq:lower-bound-mlogm}
+\end{align}
+The function $-\log \Gamma(m)$ is concave, therefore, it can be lower bounded
+by its second order Taylor series expansion as
+\begin{align}
+    -\log \Gamma(m) \geq& - \log \Gamma(m_t) - \psi(m_t) (m - m_t)\nonumber\\
+                        & - \frac{\psi'\left(\frac{1}{2}\right)}{2}(m - m_t) ^ 2,
+                        ~m \geq \frac{1}{2},~m_t \geq \frac{1}{2},
+    \label{eq:lower-bound-negloggamma}
+\end{align}
+in which $\psi(x) = \dfrac{\Gamma'(x)}{\Gamma(x)}$ is known as the digamma function.
+For both inequalities presented above, equality is achieved at $m = m_t$.
+
+Substituting (\ref{eq:lower-bound-mlogm}) and (\ref{eq:lower-bound-negloggamma}) into
+(\ref{eq:loglike}), a lower bound for $\log p(\bm{h})$ is obtained in~(\ref{eq:surrogate}).
+Due to the simple form of $g(m | m_t)$, its maximizer can be found in closed form, and
+an updating rule for the MLE can be written as
+\begin{align}
+    m_{t+1} = 1 + \dfrac{1}{\psi'(\frac{1}{2})}&\left(1 + \log \frac{m_t}{\Omega} - \psi(m_t)
+    + \right.\nonumber\\
+    &+ \left.\dfrac{1}{n} \left(2\sum_{i=1}^{n}\log h_i - \frac{\sum_{i=1}^{n}h_i^2}{\Omega}\right)\right)
+\end{align}
+
+Additionally,
+note that $m_{t+1}$ is an estimator of the true parameter value $m$. Its expected value,
+conditioned on the knowledge of $m_t$, is given as
+\begin{align}
+ \mathbb{E}(m_{t+1} | m_t) = 1 + \dfrac{1}{\psi'(\frac{1}{2})}\left(\log \frac{m_t}{\Omega} - \psi(m_t)
+    + \dfrac{2}{n}\sum_{i=1}^{n}\mathbb{E}(\log h_i)\right)
+\end{align}
+
+Its variance, also conditioned on the knowledge of $m_t$, is given as
+\begin{align}
+    \mathrm{var}(m_{t+1} | m_t) = \left(\dfrac{1}{n\psi'(\frac{1}{2})}\right)^2
+    \mathrm{var}\left(2\sum_{i=1}^{n}\log h_i
+    - \frac{\sum_{i=1}^{n}h_i^2}{\Omega}\right).
+\end{align}
+
+The Cram\'er-Rao Lower Bound for any unbiased estimator of $m$, say $\hat{m}$, is given as~\cite{cheng2001}
+\begin{align}
+    \mathrm{var}(\hat{m}) = \dfrac{1}{n\left(\psi'(m) - \frac{1}{m}\right)}
+\end{align}
+
+\begin{figure*}[!htb]
+\begin{align}
+    g(m | m_t) = n\left(-m\log\Omega  + m(1 + \log m_t) - m_t
+    -\log \Gamma(m_t) - \psi(m_t) (m - m_t) - \frac{\psi'\left(\frac{1}{2}\right)}{2}(m - m_t)^2\right)
+    -m\left(\dfrac{\sum_{i=1}^{n}h_i^2}{\Omega} - 2\sum_{i=1}^{n}\log h_i\right)
+    \label{eq:surrogate}
+\end{align}
+\end{figure*}
+
+\subsection{BER in Complex $\alpha-\mu$ Fading}
 
@@
 \begin{align}
-    y = hs + w
+    \bm{y} = h\bm{s} + \bm{w}
 \end{align}
-in which $s \in \{0, a\}$, $a \in \mathbb{R}_{+}$, is a transmitted signal,
-$h$ is an $\alpha$-$\mu$ random variable and $\bm{w}$ is a Gaussian random variable
-with zero mean vector and variance $\sigma^2$, and $y$ is the received signal.
+in which $\bm{s} \in \mathbb{C}^{n\times 1}$ is a complex On-Off Keying (OOK) signal,
+$h$ is a complex $\alpha-\mu$ random variable and $\bm{w}$ is a complex Gaussian process
+with zero mean vector and covariance matrix equals $\sigma^2\bm{I}_n$, and $\bm{y}$ is
+the received complex vector signal.
 
-Assume that the binary symbols are equiprobable, then the probability of one bit error
+Assume that the OOK symbols are equiprobable and that there exist no interference
+between the in-phase and quadrature components, then the probability of one bit error
 is given as
 \begin{align}
-    p_{e} = \dfrac{1}{2}\left(\mathbb{P}\left(\hat{y} = 0 | s = a\right)
-                            + \mathbb{P}\left(\hat{y} = 1 | s = 0\right)\right).
+    p_{e} = \dfrac{1}{2}\left(\mathbb{P}\left(\hat{y}_i = 0 | s_{i} = 1\right)
+                            + \mathbb{P}\left(\hat{y}_i = 1 | s_{i} = 0\right)\right).
 \end{align}
 
-Further, assume that the decoded bit $\hat{y}$ is estimated using the minimum distance decoding
+Assume that the decoded vector $\bm{\hat{y}}$ is estimated using the minimum distance decoding
 rule, i.e.,
-\begin{align}
-    \hat{y} = \mathbb{I}(|y - a|^2 < |y|^2)
-\end{align}
-therefore
-\begin{align}
-    \mathbb{P}\left(\hat{y} = 1 | s = 0\right) & = \mathbb{P}\left(|w - a|^2 - |w|^2 < 0\right) = 1 - \Phi\left(\frac{a}{2\sigma}\right)
-\end{align}
-and likewise
-\begin{align}
-    \mathbb{P}\left(\hat{y} = 0 | s = a\right) & = \mathbb{P}\left(ha + w < \frac{a}{2}\right) = \mathbb{E}_h\left(\Phi\left(\frac{a(1 - 2h)}{2\sigma}\right)\right).
-\end{align}
 
-In Fig.~\ref{fig:ber}, we show the expression of the BER as a function of the signal-to-noise ratio,
-for the system under consideration with $\alpha=2$ and $\mu = 5$.
-As we can see, the simulation presents an excellent agreement against theorectical results.
-\begin{figure}[!htb]
-    \centering
-    \includegraphics{figures/ber}
-    \caption{BER as a function of the SNR for $\alpha=2$ and $\mu = 5$}
-    \label{fig:ber}
-\end{figure}
+\section{Conclusions}
 
-\section{Conclusions}\label{conclusions}
-
-This paper presents a novel Python-based library for generalized fading simulation.
-The implementation is tested and validated in two use cases, namely,
-spectrum sensing and BER computation.
-
-The computational results show that the implementation presents a
-satisfactory agreement when compared with the theorectical formulation.
-
-We expect that the proposed library, which is open source,
-will be usefull to researchers, professors, and students of
-the field of wireless communications.
-
-Finally, all the simulations were done in a personal laptop,
-and the generation of $10^6$ samples from any of the generalized fading
-distributions took on average 10 seconds.
+\section*{Acknowledgement}
+The authors would like to thank the Federal University of Campina Grande (UFCG)
+and the Institute for Advanced Studies in Communications (Iecom) for supporting
+this research.
 
 \bibliographystyle{IEEEtran}
-\bibliography{manuscript}
+\bibliography{manuscript.bib}
 

### 2018-03-23 setup.py

@@ -10,7 +10,7 @@ from os import path
 if "release" in sys.argv[-1]:
     os.system("python setup.py sdist")
     os.system("twine upload dist/*")
-    os.system("rm -rf dist/yacoub*")
+    os.system("rm -rf dist/maoud*")
     sys.exit()
 
 here = path.abspath(path.dirname(__file__))
@@ -20,12 +20,12 @@ with open(path.join(here, 'README.rst'), encoding='utf-8') as f:
     long_description = f.read()
 
 setup(
-    name='yacoub',
-    packages=['yacoub'],
+    name='maoud',
+    packages=['maoud'],
     version='0.1.dev0',
-    description='Simulating fading channels in tensorflow',
+    description='Simulating generalized fading channels',
     long_description=long_description,
-    url='https://github.com/mirca/yacoub',
+    url='https://github.com/mirca/maoud',
     author='mirca',
     author_email='jvmirca@gmail.com',
     license='MIT',

### 2018-03-27 paper/manuscript.tex
add stuff

@@
 Gaussian, with zero mean vector and covariance matrix given by
-$\mathbb{E}\left[\bm{z}\bm{z}^{\dagger}\right]$, in which $\bm{z}^\dagger$ means
-the conjugate transpose of $\bm{z}$. The expectation value w.r.t. to the
+$\mathbb{E}\left(\bm{z}\bm{z}^{\dagger}\right)$, in which $\bm{z}^\dagger$ means
+the conjugate transpose of $\bm{z}$. The expectation value with respect to the
 probability distribution of a random variable $x$ is denoted as $\mathbb{E}_x$.
@@
 on the same domain $D$, $f \cong g$ means that there exist a constant $c$ such that
-$f(\bm{x}) = g(\bm{x}) + c$, $\forall~ \bm{x} \in D$.
+$f(\bm{x}) = g(\bm{x}) + c$, $\forall~ \bm{x} \in D$. The natural logarithm of a
+scalar $x > 0$ is denoted as $\log x$.
 
 \section{The Acceptance-Rejection sampler in log-space}
-
-\section{Majorization-Minimization Algorithms}
 
@@
 \begin{align}
-    p(\tilde{y} | h, H_1) = 1 - Q_{n}\left(\sqrt{\dfrac{2n|h|^2E_s}{\sigma^2}}, \sqrt{\dfrac{2\tilde{y}}{\sigma^2}}\right),
+    p(\tilde{y} | h, H_1) = 1 - \mathrm{Q}_{n}\left(\sqrt{\dfrac{2n|h|^2E_s}{\sigma^2}}, \sqrt{\dfrac{2\tilde{y}}{\sigma^2}}\right),
 \end{align}
-in which $Q_{n}$ is the Marcum-$Q$ function and $E_s$ is the energy per symbol.
+in which $\mathrm{Q}_{n}$ is the Marcum-$\mathrm{Q}$ function and $E_s$ is the energy per symbol.
 
@@
 \begin{align}
-    p(\bm{h})& = \prod_{i=1}^{n}\dfrac{2m^m}{\Gamma(m)\Omega^{m}}h_i^{2m - 1}
+    p(\bm{h} &| m, \Omega) = \prod_{i=1}^{n}\dfrac{2m^m}{\Gamma(m)\Omega^{m}}h_i^{2m - 1}
               \exp\left(-\dfrac{mh_i^2}{\Omega}\right) \nonumber \\
@@
 \end{align}
-And the log likelihood function (up to an additive constant) is given as
+And the log-likelihood function (up to an additive constant) is given as
 \begin{align}
-\log p(\bm{h}) \cong &~n\left(m\left(\log m - \log\Omega\right) - \log\Gamma(m)\right)\nonumber
-    \\ & -m\left(\dfrac{\sum_{i=1}^{n}h_i^2}{\Omega} - 2\sum_{i=1}^{n}\log h_i\right)
+\log p(\bm{h} | m, \Omega) \cong &~n\left(m\left(\log m - \log\Omega\right) - \log\Gamma(m)\right)\nonumber
+    \\ & -m\sum_{i=1}^{n}\left(\dfrac{h_i^2}{\Omega} - 2\log h_i\right)
     \label{eq:loglike}
@@
 Therefore, we use a Majorization-Minimization algorithm to find smooth
-and easy to optimize lower bounds for $\log p(\bm{h})$. More precisely,
+and easy to optimize lower bounds for $\log p(\bm{h}| m, \Omega)$. More precisely,
 we need to find lower bounds for $m\log m$ and $-\log \Gamma(m)$ for $m \geq \frac{1}{2}$.
@@
 \begin{align}
-    m_{t+1} = 1 + \dfrac{1}{\psi'(\frac{1}{2})}&\left(1 + \log \frac{m_t}{\Omega} - \psi(m_t)
-    + \right.\nonumber\\
-    &+ \left.\dfrac{1}{n} \left(2\sum_{i=1}^{n}\log h_i - \frac{\sum_{i=1}^{n}h_i^2}{\Omega}\right)\right)
+    m_{t+1} = m_t + \dfrac{1}{\psi'(\frac{1}{2})}&\left(1 + \log \frac{m_t}{\Omega} - \psi(m_t) \right.\nonumber\\
+    &\left.+ \dfrac{1}{n} \sum_{i=1}^{n}\left(2\log h_i - \frac{h_i^2}{\Omega}\right)\right)
 \end{align}
@@
 Additionally,
-note that $m_{t+1}$ is an estimator of the true parameter value $m$. Its expected value,
-conditioned on the knowledge of $m_t$, is given as
+note that $m_{t+1}$, $t \in \mathbb{N}$, is a sequence of estimators that converges to the maximum
+likelihood estimator of the parameter value $m$.
+The expected value of $m_{t+1}$, conditioned on the knowledge of $m_t$, is given as
 \begin{align}
- \mathbb{E}(m_{t+1} | m_t) = 1 + \dfrac{1}{\psi'(\frac{1}{2})}\left(\log \frac{m_t}{\Omega} - \psi(m_t)
-    + \dfrac{2}{n}\sum_{i=1}^{n}\mathbb{E}(\log h_i)\right)
+    \mathbb{E}(m_{t+1} | m_t) = m_t + \dfrac{1}{\psi'(\frac{1}{2})}\left(\log \frac{m_t}{m} + \psi(m) - \psi(m_t)\right),
+\end{align}
+in which we used the fact that~\cite{gradshteyn2007}
+\begin{align}
+    \mathbb{E}\left(\log h_i\right)~=~\frac{1}{2}\left(\psi(m)-\log\left(\frac{m}{\Omega}\right)\right).
 \end{align}
 
-Its variance, also conditioned on the knowledge of $m_t$, is given as
+Most importantly, as $m_t \rightarrow m$, then $\mathbb{E}(m_{t+1} | m_t) \rightarrow m$.
+
+The variance of $m_{t+1}$, given $m_t$, can be expressed as
 \begin{align}
-    \mathrm{var}(m_{t+1} | m_t) = \left(\dfrac{1}{n\psi'(\frac{1}{2})}\right)^2
-    \mathrm{var}\left(2\sum_{i=1}^{n}\log h_i
-    - \frac{\sum_{i=1}^{n}h_i^2}{\Omega}\right).
+    \mathrm{var}(m_{t+1} | m_t) = \dfrac{1}{n\left(\psi'(\frac{1}{2})\right)^2}
+    \mathrm{var}\left(2\log h_1 - \frac{h_1^2}{\Omega}\right).
 \end{align}
+
+\begin{align}
+    \mathbb{E}\left(\log ^ 2 h_i\right) = \frac{1}{4}\left\{\left[\psi(m) - \log\frac{m}{\Omega}\right]^2 + \zeta(2, m)\right\}
+\end{align}
+
+\begin{figure}
+    \centering
+    \includegraphics{figures/mm.eps}
+\end{figure}
 
@@
 \begin{align}
-    \mathrm{var}(\hat{m}) = \dfrac{1}{n\left(\psi'(m) - \frac{1}{m}\right)}
+    \mathrm{var}(\hat{m}) \geq \dfrac{1}{n\left(\psi'(m) - \frac{1}{m}\right)}
 \end{align}

### 2018-03-27 paper/manuscript.tex
add a little of the introduction

@@
 
+The study of wireless communications systems heavily depends on channel simulation.
+By channel simulation, we mean the generation of samples from a random variable
+which resembles the effects of real communications channels on the transmitted signal.
+
+Although accurate and precise distributions for generalized fading have been
+estabilished in the literature, such as $\alpha-\mu$, $\kappa-\mu$, and
+$\eta-\mu$, the generation of samples following these distributions is usually
+a time-consuming task. In~\cite{}, an efficient algorithm for generation of samples
+from those distributions was proposed, however, there are neither open nor
+closed source implementations available to the scientific community.
+
+In this paper, we present an open source Python package, named \texttt{maoud},
+for generation of samples following the $\alpha-\mu$, $\kappa-\mu$, and
+$\eta-\mu$ distributions. The usefullness of $\texttt{maoud}$ is illustrated
+through examples involving spectrum sensing, bit error rate computation, and
+fading estimation.
+
 \subsection*{Notation}
-Scalars and random variables are denoted as \textit{italic}, small-case letters
-\textit{e.g.} $x$; sets and events are denoted as \textit{italic}, capital
+Scalars and random variables are denoted as italic, small-case letters
+\textit{e.g.} $x$; sets and events are denoted as italic, capital
 letters \textit{e.g.}, $A$; vectors and random vectors are denoted as
-\textit{italic}, boldface, small-case letters \textit{e.g.} $\bm{x}$. The $n-$th
+italic, boldface, small-case letters \textit{e.g.} $\bm{x}$. The $n-$th
 component of a vector $\bm{x}$ is denoted as $x_n$. A complex vector of length
 $n$ is defined as $\bm{x} \in \mathbb{C}^{n\times 1}$. All vectors are column
-vectors. Matrices are denoted as \textit{italic}, boldface, capital letters as
+vectors. Matrices are denoted as italic, boldface, capital letters as
 in $\bm{X}$; the identity matrix of order $n$ is denoted as $\bm{I}_n$. We
@@
 
-\section{The Acceptance-Rejection sampler in log-space}
+\section{Rejection sampling}
 
@@
 \end{align}
-The function $-\log \Gamma(m)$ is concave, therefore, it can be lower bounded
+The function $-\log \Gamma(m)$ is concave for $m > 0$, therefore, it can be lower bounded
 by its second order Taylor series expansion as
@@
                         & - \frac{\psi'\left(\frac{1}{2}\right)}{2}(m - m_t) ^ 2,
-                        ~m \geq \frac{1}{2},~m_t \geq \frac{1}{2},
     \label{eq:lower-bound-negloggamma}
@@
 Substituting (\ref{eq:lower-bound-mlogm}) and (\ref{eq:lower-bound-negloggamma}) into
-(\ref{eq:loglike}), a lower bound for $\log p(\bm{h})$ is obtained in~(\ref{eq:surrogate}).
+(\ref{eq:loglike}), a lower bound for $\log p(\bm{h})$ is obtained as follows
+\begin{align}
+    &g(m | m_t) = n\left.\Bigg[-m\log\Omega  + m(1 + \log m_t) - m_t\right.\nonumber\\
+    & -\log \Gamma(m_t) - \psi(m_t) (m - m_t) \left. - \frac{\psi'\left(\frac{1}{2}\right)}{2}(m - m_t)^2\right]\nonumber\\
+    & -m\left(\dfrac{\sum_{i=1}^{n}h_i^2}{\Omega} - 2\sum_{i=1}^{n}\log h_i\right)
+    \label{eq:surrogate}
+\end{align}
+
 Due to the simple form of $g(m | m_t)$, its maximizer can be found in closed form, and
@@
 \begin{align}
-    m_{t+1} = m_t + \dfrac{1}{\psi'(\frac{1}{2})}&\left(1 + \log \frac{m_t}{\Omega} - \psi(m_t) \right.\nonumber\\
+    m_{t+1} = m_t + \dfrac{1}{\psi'(\frac{1}{2})}&\left.\Bigg(1 + \log \frac{m_t}{\Omega} - \psi(m_t) \right.\nonumber\\
     &\left.+ \dfrac{1}{n} \sum_{i=1}^{n}\left(2\log h_i - \frac{h_i^2}{\Omega}\right)\right)
@@
 \begin{align}
-    \mathbb{E}\left(\log ^ 2 h_i\right) = \frac{1}{4}\left\{\left[\psi(m) - \log\frac{m}{\Omega}\right]^2 + \zeta(2, m)\right\}
+    \mathbb{E}\left(\log ^ 2 h_1\right) &= \frac{1}{4}\left\{\left[\psi(m) - \log\frac{m}{\Omega}\right]^2 + \zeta(2, m)\right\}\\
+    \mathbb{E}\left(h_1^2\log h_1\right) &= \frac{\Omega}{2}\left(\psi(m+1) - \log\frac{m}{\Omega}\right)\\
+    \mathbb{E}\left(h_1^2\right) &= \Omega\\
+    \mathbb{E}\left(h_1^4\right) &= \Omega^2\frac{m+1}{m}
+\end{align}
+
+\begin{align}
+    \mathrm{var}(m_{t+1} | m_t) = \dfrac{\zeta(2, m) + \frac{1}{m} + 2 (\psi(m) - \psi(m+1))}{n\left(\psi'(\frac{1}{2})\right)^2}
 \end{align}
@@
 \end{align}
-
-\begin{figure*}[!htb]
-\begin{align}
-    g(m | m_t) = n\left(-m\log\Omega  + m(1 + \log m_t) - m_t
-    -\log \Gamma(m_t) - \psi(m_t) (m - m_t) - \frac{\psi'\left(\frac{1}{2}\right)}{2}(m - m_t)^2\right)
-    -m\left(\dfrac{\sum_{i=1}^{n}h_i^2}{\Omega} - 2\sum_{i=1}^{n}\log h_i\right)
-    \label{eq:surrogate}
-\end{align}
-\end{figure*}
 

### 2018-04-20 paper/manuscript.tex
push stuff

--- 2018-03-27 paper/manuscript.tex
@@
 \usepackage{tabularx,colortbl}
+\DeclareMathOperator*{\argmin}{arg\,min}
 
@@
 Campina Grande, Para\'iba, Brasil\\
-\{josevinicius,paulo,wamberto,malencar\}@iecom.org.br\\}
+\{josevinicius, wamberto, paulo, malencar\}@iecom.org.br\\}
 }
@@
     estimation of the fading parameter. The development of \texttt{maoud} is open
-    source and its code along with examples are avaliable at
-    \texttt{http://github.com/mirca/maoud}.
+    source and its code, along with the code for the examples presented in this
+    paper, are avaliable at \texttt{http://github.com/mirca/maoud}.
 \end{abstract}
@@
 
+The study of modern wireless communications systems heavily relies on fading channel simulation.
+By fading channel simulation, we refer to the generation of samples from a probability distribution
+that resembles the effects and impairments caused by real communications fading channels on the
+transmitted signal.
+
+Although accurate and precise distributions for generalized fading have been
+estabilished in the literature, such as $\alpha\text{-}\mu$~\cite{yacoub.2007.1},
+$\kappa\text{-}\mu$~\cite{yacoub.2007.2} and $\eta\text{-}\mu$~\cite{yacoub.2007.2},
+the generation of samples following these distributions is usually
+a time-consuming task. In~\cite{cogliatti2012}, the authors built an efficient
+algorithm, based on the rejection method, for generation of samples from those
+distributions.
+
+however, there are neither open nor
+closed source implementations available to the scientific community.
+
+In this paper, we present an open source Python package, named \texttt{maoud},
+for generation of samples following the $\alpha\text{-}\mu$, $\kappa\text{-}\mu$, and
+$\eta\text{-}\mu$ distributions. The usefullness of $\texttt{maoud}$ is illustrated
+through examples involving spectrum sensing, bit error rate (BER) computation, and
+fading estimation.
+
 \subsection*{Notation}
-Scalars and random variables are denoted as \textit{italic}, small-case letters
-\textit{e.g.} $x$; sets and events are denoted as \textit{italic}, capital
+Scalars and random variables are denoted as italic, small-case letters
+\textit{e.g.} $x$; sets and events are denoted as italic, capital
 letters \textit{e.g.}, $A$; vectors and random vectors are denoted as
-\textit{italic}, boldface, small-case letters \textit{e.g.} $\bm{x}$. The $n-$th
+italic, boldface, small-case letters \textit{e.g.} $\bm{x}$. The $n-$th
 component of a vector $\bm{x}$ is denoted as $x_n$. A complex vector of length
 $n$ is defined as $\bm{x} \in \mathbb{C}^{n\times 1}$. All vectors are column
-vectors. Matrices are denoted as \textit{italic}, boldface, capital letters as
+vectors. Matrices are denoted as italic, boldface, capital letters as
 in $\bm{X}$; the identity matrix of order $n$ is denoted as $\bm{I}_n$. We
@@
 \end{align}
-in which $\bm{y} \in \mathbb{C}^{n\times 1}$ is the decoded received vector signal,
+in which $\bm{y} \in \mathbb{C}^{n\times 1}$ is the received vector signal,
 $\bm{w} \in \mathbb{C}^{n\times 1}$ is complex Gaussian noise process with zero mean
@@
 
-In~\cite{cardoso2017}, the authors have shown that the probability distribution of the
+In~\cite{cardoso2017}, the authors have shown that the cumulative distribution function (cdf) of the
 energy statistic $\tilde{y} \triangleq \bm{y}^{\dagger}\bm{y}$ conditioned on the knowledge of $h$,
@@
 \begin{align}
-    p(\tilde{y} | h, H_1) = 1 - \mathrm{Q}_{n}\left(\sqrt{\dfrac{2n|h|^2E_s}{\sigma^2}}, \sqrt{\dfrac{2\tilde{y}}{\sigma^2}}\right),
+    P(\tilde{y} | h, H_1) = 1 - \mathrm{Q}_{n}\left(\sqrt{\dfrac{2n|h|^2E_s}{\sigma^2}}, \sqrt{\dfrac{2\tilde{y}}{\sigma^2}}\right),
 \end{align}
 in which $\mathrm{Q}_{n}$ is the Marcum-$\mathrm{Q}$ function and $E_s$ is the energy per symbol.
-
-The pdf of $\tilde{y}$ can be written using the Law of Total Expectation
-\begin{align}
-    p(\tilde{y} | H_1) = \mathbb{E}_{h}\left[p(\tilde{y} | h, H_{1})\right]
-                 = \int_{-\infty}^{+\infty} p(\tilde{y} | h, H_1)p(h)\;\mathrm{d}h.
-\end{align}
 
@@
     d_\delta (\tilde{y}) = \mathbb{I}(\tilde{y} > \delta)
-\right.
 \end{equation}
@@
 \begin{align}
-    p_f &\triangleq \mathbb{P}\left(d_\delta(\tilde{y}) = 1 | H_0\right) = 1 -  p(\delta | H_0),\label{eq:pf} \\
-    p_d &\triangleq \mathbb{P}\left(d_\delta(\tilde{y}) = 0 | H_1\right) = \mathbb{E}_{h}\left[p(\delta, h | H_1)\right],
-\label{eq:pd}
+    \mathbb{P}\left(d_\delta(\tilde{y}) = 1 | H_0\right) &=
+        1 -  P(\delta | H_0) = 1 - \gamma\left(n, \frac{\delta}{\sigma^2}\right),\label{eq:pf} \\
+    \mathbb{P}\left(d_\delta(\tilde{y}) = 0 | H_1\right) &= \mathbb{E}_{h}\left(P(\delta| h, H_1)\right)\nonumber\\
+    &= \int_{-\infty}^{+\infty} P(\delta | h, H_1)p(h)\;\mathrm{d}h,\label{eq:pd}
 \end{align}
+in which $\gamma$ is the regularized lower incomplete Gamma function, $p(h)$ is the pdf of the fading,
+and $\delta$ is the energy detection threshold.
+
+The performance of detection schemes can be measured by computing the Receiver Operating
+Characteristic (ROC), which consists in varying $\delta$ and computing the pairs of
+probability of false alarm and miss detection, as illustrated in Fig.~\ref{fig:spectrum-sensing}.
+
+\begin{figure}[!htb]
+    \centering
+    \includegraphics{figures/spectrum_sensing.eps}
+    \caption{Receiver Operating Characteristic for the energy detector in $\alpha$-$\mu$
+             fading channel with $\alpha=2$ and $\mu=1$, i.e., Nakagami-$m$, $m = 1$.
+             The solid curve represents the theorectical probabilities as stated on
+             (\ref{eq:pf}) and (\ref{eq:pd}) for different values of
+             $\delta$, whereas bullets represent Monte Carlo simulations acquired with $10^6$ realizations.
+             The input signal $\bm{s}$ consists in a vector of length $n=25$ in which each entry represents
+             a symbol of a 64-PSK constellation. Symbols are assumed to be equiprobable.
+             The signal-to-noise ratio is set to $5$ dB.}
+    \label{fig:spectrum-sensing}
+\end{figure}
 
@@
 \begin{align}
-    p(\bm{h} &| m, \Omega) = \prod_{i=1}^{n}\dfrac{2m^m}{\Gamma(m)\Omega^{m}}h_i^{2m - 1}
+    p(\bm{h} &| m) = \prod_{i=1}^{n}\dfrac{2m^m}{\Gamma(m)\Omega^{m}}h_i^{2m - 1}
               \exp\left(-\dfrac{mh_i^2}{\Omega}\right) \nonumber \\
           = & \left(\dfrac{2m^m}{\Gamma(m)\Omega^{m}}\right)^{n}
-          \exp\left(-\dfrac{m\sum_{i=1}^{n}h_i^2}{\Omega}\right) \prod_{i=1}^{n}h_i^{2m - 1}
+          \exp\left(-\dfrac{m\sum_{i=1}^{n}h_i^2}{\Omega}\right) \prod_{i=1}^{n}h_i^{2m - 1},
 \end{align}
-And the log-likelihood function (up to an additive constant) is given as
+in which $m$ is the fading parameter and $\Omega = \mathbb{E}(h_i^2)$ is the scale parameter.
+
+The negative log-likelihood function (up to an additive constant) is given as
 \begin{align}
-\log p(\bm{h} | m, \Omega) \cong &~n\left(m\left(\log m - \log\Omega\right) - \log\Gamma(m)\right)\nonumber
-    \\ & -m\sum_{i=1}^{n}\left(\dfrac{h_i^2}{\Omega} - 2\log h_i\right)
+-\log p(\bm{h} | m) \cong &-n\left(m\left(\log m - \log\Omega\right) - \log\Gamma(m)\right)\nonumber
+    \\ & +m\sum_{i=1}^{n}\left(\dfrac{h_i^2}{\Omega} - 2\log h_i\right).
     \label{eq:loglike}
@@
 A direct maximum likelihood estimator (MLE) for (\ref{eq:loglike}) has been
-investigated to be infeasible~\cite{cheng2001}.
+shown to be infeasible~\cite{cheng2001}. Thus, we use the
+Majorization-Minimization technique~\cite{sun2016} to find smooth
+and easy to optimize upper bounds for $-\log p(\bm{h}| m)$.
 
-Therefore, we use a Majorization-Minimization algorithm to find smooth
-and easy to optimize lower bounds for $\log p(\bm{h}| m, \Omega)$. More precisely,
-we need to find lower bounds for $m\log m$ and $-\log \Gamma(m)$ for $m \geq \frac{1}{2}$.
-The former function is convex for $m \geq 0$, hence it can be lower bounded
+Basically, the Majorization-Minimization (MM) algorithm consists in constructing a
+sequence of functions $g(\cdot | m_t)$, initiliazed at $m_0$, such that
+\begin{align}
+    g(m | m_t) &\geq -\log p(\bm{h}| m) + c_t\label{eq:majorization-step},\\
+    c_t &= g(m_t | m_t) + \log p(\bm{h}| m)\label{eq:mid-step},\\
+    m_{t+1} &\in \argmin_{m > \frac{1}{2}} g(m | m_t)\label{eq:minimization-step}.
+\end{align}
+Note that (\ref{eq:majorization-step}) is the majorization step and (\ref{eq:minimization-step})
+is the minimization step, whereas (\ref{eq:mid-step}) is a condition to ensure that the difference
+of $g(\cdot | m_t)$ and $-\log p(\bm{h}| \cdot)$ is minimized at $m_t$.
+
+Therefore, one possible way to construct $g(\cdot|m_t)$ is to find upper bounds for
+$-m\log m$ and $\log \Gamma(m)$ for $m \geq \frac{1}{2}$.
+The former function is concave for $m \geq 0$, hence it can be upper bounded
 by its first order Taylor series as
 \begin{align}
-    m \log m \geq m(1 + \log m_t) - m_t,
-    \label{eq:lower-bound-mlogm}
+    -m \log m \leq -m(1 + \log m_t) + m_t,
+    \label{eq:upper-bound-mlogm}
 \end{align}
-The function $-\log \Gamma(m)$ is concave, therefore, it can be lower bounded
+The function $\log \Gamma(m)$ is convex for $m > 0$, therefore, it can be upper bounded
 by its second order Taylor series expansion as
 \begin{align}
-    -\log \Gamma(m) \geq& - \log \Gamma(m_t) - \psi(m_t) (m - m_t)\nonumber\\
-                        & - \frac{\psi'\left(\frac{1}{2}\right)}{2}(m - m_t) ^ 2,
-                        ~m \geq \frac{1}{2},~m_t \geq \frac{1}{2},
-    \label{eq:lower-bound-negloggamma}
+    \log \Gamma(m) \leq&  \log \Gamma(m_t) + \psi(m_t) (m - m_t)\nonumber\\
+                        &  + \frac{\psi'\left(\frac{1}{2}\right)}{2}(m - m_t) ^ 2,
+    \label{eq:upper-bound-negloggamma}
 \end{align}
@@
 
-Substituting (\ref{eq:lower-bound-mlogm}) and (\ref{eq:lower-bound-negloggamma}) into
-(\ref{eq:loglike}), a lower bound for $\log p(\bm{h})$ is obtained in~(\ref{eq:surrogate}).
-Due to the simple form of $g(m | m_t)$, its maximizer can be found in closed form, and
+Applying inequalities (\ref{eq:upper-bound-mlogm}) and (\ref{eq:upper-bound-negloggamma}) into
+(\ref{eq:loglike}), an upper bound for $\log p(\bm{h})$ is obtained as follows
+\begin{align}
+    &g(m | m_t) = - n\left.\Bigg[-m\log\Omega  + m(1 + \log m_t) - m_t\right.\nonumber\\
+    & -\log \Gamma(m_t) - \psi(m_t) (m - m_t) \left. - \frac{\psi'\left(\frac{1}{2}\right)}{2}(m - m_t)^2\right]\nonumber\\
+    & +m\left(\dfrac{\sum_{i=1}^{n}h_i^2}{\Omega} - 2\sum_{i=1}^{n}\log h_i\right)
+    \label{eq:surrogate}
+\end{align}
+
+Due to the simple form of $g(m | m_t)$, its minimizer can be found in closed form, and
 an updating rule for the MLE can be written as
 \begin{align}
-    m_{t+1} = m_t + \dfrac{1}{\psi'(\frac{1}{2})}&\left(1 + \log \frac{m_t}{\Omega} - \psi(m_t) \right.\nonumber\\
-    &\left.+ \dfrac{1}{n} \sum_{i=1}^{n}\left(2\log h_i - \frac{h_i^2}{\Omega}\right)\right)
+    m_{t+1} = m_t + \dfrac{1}{\psi'(\frac{1}{2})}&\left.\Bigg(1 + \log \frac{m_t}{\Omega} - \psi(m_t) \right.\nonumber\\
+    &\left.+ \dfrac{1}{n} \sum_{i=1}^{n}\left(2\log h_i - \frac{h_i^2}{\Omega}\right)\right).
 \end{align}
@@
 Additionally,
-note that $m_{t+1}$, $t \in \mathbb{N}$, is a sequence of estimators that converges to the maximum
-likelihood estimator of the parameter value $m$.
-The expected value of $m_{t+1}$, conditioned on the knowledge of $m_t$, is given as
+note that $\left\{m_{t+1}\right\}_{t \in \mathbb{N}}$ is a sequence of
+estimators that converges to the MLE of the parameter value $m$. This
+fact is a consequence of the convergence properties of the MM algorithm~\cite{sun2016}.
+Therefore, the proposed estimator is asymptotically consistent and efficient.
+
+We experimentally note, and it is also illustrated in Fig~\ref{fig:mm-example}, that the
+estimator takes on average 30 iterations to converge within an absolute tolerance of $10^{-4}$.
+\begin{figure}[!htb]
+    \centering
+    \includegraphics{figures/mm.eps}
+    \caption{Typical convergence behavior of the proposed estimator.}
+    \label{fig:mm-example}
+\end{figure}
+
+Moreover, we perform an experimental analysis of the bias and variance of the proposed estimator.
+First, we recall that the Cram\'er-Rao Lower Bound for any unbiased estimator of $m$, say $\hat{m}$,
+is given as~\cite{cheng2001}
 \begin{align}
-    \mathbb{E}(m_{t+1} | m_t) = m_t + \dfrac{1}{\psi'(\frac{1}{2})}\left(\log \frac{m_t}{m} + \psi(m) - \psi(m_t)\right),
-\end{align}
-in which we used the fact that~\cite{gradshteyn2007}
-\begin{align}
-    \mathbb{E}\left(\log h_i\right)~=~\frac{1}{2}\left(\psi(m)-\log\left(\frac{m}{\Omega}\right)\right).
+    \mathrm{var}(\hat{m}) \geq \dfrac{1}{n\left(\psi'(m) - \frac{1}{m}\right)}.
 \end{align}
 
-Most importantly, as $m_t \rightarrow m$, then $\mathbb{E}(m_{t+1} | m_t) \rightarrow m$.
-
-The variance of $m_{t+1}$, given $m_t$, can be expressed as
-\begin{align}
-    \mathrm{var}(m_{t+1} | m_t) = \dfrac{1}{n\left(\psi'(\frac{1}{2})\right)^2}
-    \mathrm{var}\left(2\log h_1 - \frac{h_1^2}{\Omega}\right).
-\end{align}
-
-\begin{align}
-    \mathbb{E}\left(\log ^ 2 h_i\right) = \frac{1}{4}\left\{\left[\psi(m) - \log\frac{m}{\Omega}\right]^2 + \zeta(2, m)\right\}
-\end{align}
-
-\begin{figure}
+\begin{figure}[!htb]
     \centering
-    \includegraphics{figures/mm.eps}
+    \includegraphics{figures/bias_N100.eps}
+    \caption{Bias of the proposed estimator and the estimator presented in~\cite{cheng2001}.
+             The bias was computed via Monte Carlo simulation with $10^4$ realizations.}
+    \label{fig:bias}
 \end{figure}
 
-The Cram\'er-Rao Lower Bound for any unbiased estimator of $m$, say $\hat{m}$, is given as~\cite{cheng2001}
-\begin{align}
-    \mathrm{var}(\hat{m}) \geq \dfrac{1}{n\left(\psi'(m) - \frac{1}{m}\right)}
-\end{align}
+\begin{figure}[!htb]
+    \centering
+    \includegraphics{figures/variance_N100.eps}
+    \caption{Variance of the proposed estimator and the estimator presented in~\cite{cheng2001}
+             compared against the Cram\'er-Rao Lower Bound. The variance was computed via
+             Monte Carlo simulation with $10^4$ realizations.}
+    \label{fig:variance}
+\end{figure}
 
-\begin{figure*}[!htb]
-\begin{align}
-    g(m | m_t) = n\left(-m\log\Omega  + m(1 + \log m_t) - m_t
-    -\log \Gamma(m_t) - \psi(m_t) (m - m_t) - \frac{\psi'\left(\frac{1}{2}\right)}{2}(m - m_t)^2\right)
-    -m\left(\dfrac{\sum_{i=1}^{n}h_i^2}{\Omega} - 2\sum_{i=1}^{n}\log h_i\right)
-    \label{eq:surrogate}
-\end{align}
-\end{figure*}
+%Moreover, the expected value of $m_{t+1}$, conditioned on the knowledge of $m_t$, is given as
+%\begin{align}
+%    \mathbb{E}(m_{t+1} | m_t) = m_t + \dfrac{1}{\psi'(\frac{1}{2})}\left(\log \frac{m_t}{m} + \psi(m) - \psi(m_t)\right),
+%\end{align}
+%in which we used the fact that~\cite{gradshteyn2007}
+%\begin{align}
+%    \mathbb{E}\left(\log h_i\right)~=~\frac{1}{2}\left(\psi(m)-\log\left(\frac{m}{\Omega}\right)\right).
+%\end{align}
+%
+%Most importantly, as $m_t \rightarrow m_{MLE}$ (due to convergence property of MM),
+%then $\mathbb{E}(m_{t+1} | m_t) \rightarrow m_{MLE}$.
+%
+%The variance of $m_{t+1}$, given $m_t$, can be expressed as
+%\begin{align}
+%    \mathrm{var}(m_{t+1} | m_t) = \dfrac{\psi'(m) - \frac{1}{m}}{n\left(\psi'(\frac{1}{2})\right)^2}
+%\end{align}
+%
+%\begin{align}
+%    \mathbb{E}\left(\log ^ 2 h_1\right) &= \frac{1}{4}\left\{\left[\psi(m) - \log\frac{m}{\Omega}\right]^2 + \psi'(m)\right\}\\
+%    \mathbb{E}\left(h_1^2\log h_1\right) &= \frac{\Omega}{2}\left(\psi(m+1) - \log\frac{m}{\Omega}\right)\\
+%    \mathbb{E}\left(h_1^2\right) &= \Omega\\
+%    \mathbb{E}\left(h_1^4\right) &= \Omega^2\frac{m+1}{m}
+%\end{align}
 
-\subsection{BER in Complex $\alpha-\mu$ Fading}
+\subsection{BER in $\alpha$-$\mu$ Fading}
 
@@
 \begin{align}
-    \bm{y} = h\bm{s} + \bm{w}
+    y = hs + w
 \end{align}
-in which $\bm{s} \in \mathbb{C}^{n\times 1}$ is a complex On-Off Keying (OOK) signal,
-$h$ is a complex $\alpha-\mu$ random variable and $\bm{w}$ is a complex Gaussian process
-with zero mean vector and covariance matrix equals $\sigma^2\bm{I}_n$, and $\bm{y}$ is
-the received complex vector signal.
+in which $s \in \{0, a\}$, $a \in \mathbb{R}_{+}$, is a transmitted signal,
+$h$ is an $\alpha$-$\mu$ random variable and $\bm{w}$ is a Gaussian random variable
+with zero mean vector and variance $\sigma^2$, and $y$ is the received signal.
 
-Assume that the OOK symbols are equiprobable and that there exist no interference
-between the in-phase and quadrature components, then the probability of one bit error
+Assume that the binary symbols are equiprobable, then the probability of one bit error
 is given as
 \begin{align}
-    p_{e} = \dfrac{1}{2}\left(\mathbb{P}\left(\hat{y}_i = 0 | s_{i} = 1\right)
-                            + \mathbb{P}\left(\hat{y}_i = 1 | s_{i} = 0\right)\right).
+    p_{e} = \dfrac{1}{2}\left(\mathbb{P}\left(\hat{y} = 0 | s = a\right)
+                            + \mathbb{P}\left(\hat{y} = 1 | s = 0\right)\right).
 \end{align}
 
-Assume that the decoded vector $\bm{\hat{y}}$ is estimated using the minimum distance decoding
+Further, assume that the decoded bit $\hat{y}$ is estimated using the minimum distance decoding
 rule, i.e.,
+\begin{align}
+    \hat{y} = \mathbb{I}(|y - a|^2 < |y|^2)
+\end{align}
+therefore
+\begin{align}
+    \mathbb{P}\left(\hat{y} = 1 | s = 0\right) & = \mathbb{P}\left(|w - a|^2 - |w|^2 < 0\right)\nonumber\\
+    & = \mathbb{P}\left(w > \frac{a}{2}\right) = 1 - \Phi\left(\frac{a}{2\sigma}\right)
+\end{align}
+and likewise
+\begin{align}
+    \mathbb{P}\left(\hat{y} = 0 | s = a\right) & = \mathbb{P}\left(ha + w < \frac{a}{2}\right) \nonumber\\
+    & = \mathbb{E}_h\left(\Phi\left(\frac{a(1 - 2h)}{2\sigma}\right)\right).
+\end{align}
+
+\begin{figure}[!htb]
+    \centering
+    \includegraphics{figures/ber.eps}
+    \caption{BER}
+    \label{fig:ber}
+\end{figure}
 
 \section{Conclusions}
-
-\section*{Acknowledgement}
-The authors would like to thank the Federal University of Campina Grande (UFCG)
-and the Institute for Advanced Studies in Communications (Iecom) for supporting
-this research.
 

### 2018-04-20 maoud/__init__.py

@@ -1,2 +1,3 @@
 from .distributions import *
 from .sampling import *
+from .utils import *

### 2018-04-20 maoud/distributions.py

@@ -36,7 +36,7 @@ class Distribution(ABC):
         size : int
             Size of the sample (number of realizations).
         """
-        return rejection_sampling(self.pdf, x, size)
+        return rejection_sampling(self.pdf, x, size)[0]
 
 
 class ComplexDistribution(Distribution):
@@ -60,8 +60,11 @@ class ComplexDistribution(Distribution):
         if len(x) != len(y):
             raise ValueError("x and y must have the same length.")
 
-        return (rejection_sampling(self.pdf, x, size)
-                + 1j * rejection_sampling(self.pdf, y, size))
+        return (rejection_sampling(self.pdf, x, size)[0]
+                + 1j * rejection_sampling(self.pdf, y, size)[0])
+
+    def envelope_pdf(self, x):
+        pass
 
 
 class AlphaMu(Distribution):
@@ -152,6 +155,9 @@ class ComplexAlphaMu(ComplexDistribution):
         return (self.mu ** (self.mu * 0.5) * np.abs(x) ** (self.mu - 1.0) * np.exp(-self.mu * x * x)
                 / sps.gamma(self.mu * 0.5))
 
+    def envelope_pdf(self, x):
+        return AlphaMu(self.alpha, self.mu).pdf(x)
+
 class ComplexEtaMu(ComplexDistribution):
     def __init__(self, eta, mu):
         self.eta = eta
@@ -159,7 +165,7 @@ class ComplexEtaMu(ComplexDistribution):
 
     def pdf(self, x):
         return ((2.0 * self.mu) ** self.mu * np.abs(x) ** (2.0 * self.mu - 1.0)
-                * np.exp(-2.0 * self.mu * x * x/ (1.0 - self.eta))
+                * np.exp(-2.0 * self.mu * x * x / (1.0 - self.eta))
                 / (sps.gamma(self.mu) * np.power(1.0 - self.eta, self.mu)))
 
 
@@ -186,5 +192,5 @@ class ComplexKappaMu(object):
                 / (2.0 * sigma2 * np.abs(q) ** (0.5 * self.mu - 1.0) * np.cosh(q * x / sigma2)))
 
     def rvs(self, x, y, size):
-        return (rejection_sampling(self.real_part, x, y, size)
-                + 1j * rejection_sampling(self.imag_part, x, y, size))
+        return (rejection_sampling(self.real_part, x, y, size)[0]
+                + 1j * rejection_sampling(self.imag_part, x, y, size)[0])

### 2018-04-20 maoud/sampling.py

@@ -31,11 +31,13 @@ def rejection_sampling(pdf, x, n_samples, *args):
     n_samples = int(n_samples)
     x_min, x_max = np.min(x), np.max(x)
     accepted_samples = []
+    acceptance_fraction = []
 
     while len(accepted_samples) < n_samples:
         unif_x = np.random.uniform(low=x_min, high=x_max, size=n_samples)
         unif_y = np.random.uniform(low=pdf_min, high=pdf_max, size=n_samples)
         accept = unif_y <= pdf(unif_x, *args)
         accepted_samples = np.concatenate([accepted_samples, unif_x[accept]])
+        acceptance_fraction = np.concatenate([acceptance_fraction, [np.sum(accept)/n_samples]])
 
-    return accepted_samples[:n_samples]
+    return accepted_samples[:n_samples], acceptance_fraction

### 2018-04-20 paper/manuscript.tex
update paper

@@
 
-\subsection{Parameter Estimation in Nakagami-$m$ fading}
-The Nakagami-$m$ density is given as
-\begin{align}
-    p(\bm{h} &| m) = \prod_{i=1}^{n}\dfrac{2m^m}{\Gamma(m)\Omega^{m}}h_i^{2m - 1}
-              \exp\left(-\dfrac{mh_i^2}{\Omega}\right) \nonumber \\
-          = & \left(\dfrac{2m^m}{\Gamma(m)\Omega^{m}}\right)^{n}
-          \exp\left(-\dfrac{m\sum_{i=1}^{n}h_i^2}{\Omega}\right) \prod_{i=1}^{n}h_i^{2m - 1},
-\end{align}
-in which $m$ is the fading parameter and $\Omega = \mathbb{E}(h_i^2)$ is the scale parameter.
-
-The negative log-likelihood function (up to an additive constant) is given as
-\begin{align}
--\log p(\bm{h} | m) \cong &-n\left(m\left(\log m - \log\Omega\right) - \log\Gamma(m)\right)\nonumber
-    \\ & +m\sum_{i=1}^{n}\left(\dfrac{h_i^2}{\Omega} - 2\log h_i\right).
-    \label{eq:loglike}
-\end{align}
-
-A direct maximum likelihood estimator (MLE) for (\ref{eq:loglike}) has been
-shown to be infeasible~\cite{cheng2001}. Thus, we use the
-Majorization-Minimization technique~\cite{sun2016} to find smooth
-and easy to optimize upper bounds for $-\log p(\bm{h}| m)$.
-
-Basically, the Majorization-Minimization (MM) algorithm consists in constructing a
-sequence of functions $g(\cdot | m_t)$, initiliazed at $m_0$, such that
-\begin{align}
-    g(m | m_t) &\geq -\log p(\bm{h}| m) + c_t\label{eq:majorization-step},\\
-    c_t &= g(m_t | m_t) + \log p(\bm{h}| m)\label{eq:mid-step},\\
-    m_{t+1} &\in \argmin_{m > \frac{1}{2}} g(m | m_t)\label{eq:minimization-step}.
-\end{align}
-Note that (\ref{eq:majorization-step}) is the majorization step and (\ref{eq:minimization-step})
-is the minimization step, whereas (\ref{eq:mid-step}) is a condition to ensure that the difference
-of $g(\cdot | m_t)$ and $-\log p(\bm{h}| \cdot)$ is minimized at $m_t$.
-
-Therefore, one possible way to construct $g(\cdot|m_t)$ is to find upper bounds for
-$-m\log m$ and $\log \Gamma(m)$ for $m \geq \frac{1}{2}$.
-The former function is concave for $m \geq 0$, hence it can be upper bounded
-by its first order Taylor series as
-\begin{align}
-    -m \log m \leq -m(1 + \log m_t) + m_t,
-    \label{eq:upper-bound-mlogm}
-\end{align}
-The function $\log \Gamma(m)$ is convex for $m > 0$, therefore, it can be upper bounded
-by its second order Taylor series expansion as
-\begin{align}
-    \log \Gamma(m) \leq&  \log \Gamma(m_t) + \psi(m_t) (m - m_t)\nonumber\\
-                        &  + \frac{\psi'\left(\frac{1}{2}\right)}{2}(m - m_t) ^ 2,
-    \label{eq:upper-bound-negloggamma}
-\end{align}
-in which $\psi(x) = \dfrac{\Gamma'(x)}{\Gamma(x)}$ is known as the digamma function.
-For both inequalities presented above, equality is achieved at $m = m_t$.
-
-Applying inequalities (\ref{eq:upper-bound-mlogm}) and (\ref{eq:upper-bound-negloggamma}) into
-(\ref{eq:loglike}), an upper bound for $\log p(\bm{h})$ is obtained as follows
-\begin{align}
-    &g(m | m_t) = - n\left.\Bigg[-m\log\Omega  + m(1 + \log m_t) - m_t\right.\nonumber\\
-    & -\log \Gamma(m_t) - \psi(m_t) (m - m_t) \left. - \frac{\psi'\left(\frac{1}{2}\right)}{2}(m - m_t)^2\right]\nonumber\\
-    & +m\left(\dfrac{\sum_{i=1}^{n}h_i^2}{\Omega} - 2\sum_{i=1}^{n}\log h_i\right)
-    \label{eq:surrogate}
-\end{align}
-
-Due to the simple form of $g(m | m_t)$, its minimizer can be found in closed form, and
-an updating rule for the MLE can be written as
-\begin{align}
-    m_{t+1} = m_t + \dfrac{1}{\psi'(\frac{1}{2})}&\left.\Bigg(1 + \log \frac{m_t}{\Omega} - \psi(m_t) \right.\nonumber\\
-    &\left.+ \dfrac{1}{n} \sum_{i=1}^{n}\left(2\log h_i - \frac{h_i^2}{\Omega}\right)\right).
-\end{align}
-
-Additionally,
-note that $\left\{m_{t+1}\right\}_{t \in \mathbb{N}}$ is a sequence of
-estimators that converges to the MLE of the parameter value $m$. This
-fact is a consequence of the convergence properties of the MM algorithm~\cite{sun2016}.
-Therefore, the proposed estimator is asymptotically consistent and efficient.
-
-We experimentally note, and it is also illustrated in Fig~\ref{fig:mm-example}, that the
-estimator takes on average 30 iterations to converge within an absolute tolerance of $10^{-4}$.
-\begin{figure}[!htb]
-    \centering
-    \includegraphics{figures/mm.eps}
-    \caption{Typical convergence behavior of the proposed estimator.}
-    \label{fig:mm-example}
-\end{figure}
-
-Moreover, we perform an experimental analysis of the bias and variance of the proposed estimator.
-First, we recall that the Cram\'er-Rao Lower Bound for any unbiased estimator of $m$, say $\hat{m}$,
-is given as~\cite{cheng2001}
-\begin{align}
-    \mathrm{var}(\hat{m}) \geq \dfrac{1}{n\left(\psi'(m) - \frac{1}{m}\right)}.
-\end{align}
-
-\begin{figure}[!htb]
-    \centering
-    \includegraphics{figures/bias_N100.eps}
-    \caption{Bias of the proposed estimator and the estimator presented in~\cite{cheng2001}.
-             The bias was computed via Monte Carlo simulation with $10^4$ realizations.}
-    \label{fig:bias}
-\end{figure}
-
-\begin{figure}[!htb]
-    \centering
-    \includegraphics{figures/variance_N100.eps}
-    \caption{Variance of the proposed estimator and the estimator presented in~\cite{cheng2001}
-             compared against the Cram\'er-Rao Lower Bound. The variance was computed via
-             Monte Carlo simulation with $10^4$ realizations.}
-    \label{fig:variance}
-\end{figure}
-
-%Moreover, the expected value of $m_{t+1}$, conditioned on the knowledge of $m_t$, is given as
-%\begin{align}
-%    \mathbb{E}(m_{t+1} | m_t) = m_t + \dfrac{1}{\psi'(\frac{1}{2})}\left(\log \frac{m_t}{m} + \psi(m) - \psi(m_t)\right),
-%\end{align}
-%in which we used the fact that~\cite{gradshteyn2007}
-%\begin{align}
-%    \mathbb{E}\left(\log h_i\right)~=~\frac{1}{2}\left(\psi(m)-\log\left(\frac{m}{\Omega}\right)\right).
-%\end{align}
-%
-%Most importantly, as $m_t \rightarrow m_{MLE}$ (due to convergence property of MM),
-%then $\mathbb{E}(m_{t+1} | m_t) \rightarrow m_{MLE}$.
-%
-%The variance of $m_{t+1}$, given $m_t$, can be expressed as
-%\begin{align}
-%    \mathrm{var}(m_{t+1} | m_t) = \dfrac{\psi'(m) - \frac{1}{m}}{n\left(\psi'(\frac{1}{2})\right)^2}
-%\end{align}
-%
-%\begin{align}
-%    \mathbb{E}\left(\log ^ 2 h_1\right) &= \frac{1}{4}\left\{\left[\psi(m) - \log\frac{m}{\Omega}\right]^2 + \psi'(m)\right\}\\
-%    \mathbb{E}\left(h_1^2\log h_1\right) &= \frac{\Omega}{2}\left(\psi(m+1) - \log\frac{m}{\Omega}\right)\\
-%    \mathbb{E}\left(h_1^2\right) &= \Omega\\
-%    \mathbb{E}\left(h_1^4\right) &= \Omega^2\frac{m+1}{m}
-%\end{align}
-
 \subsection{BER in $\alpha$-$\mu$ Fading}

### 2018-04-20 paper/manuscript.tex
update paper

@@
 
-\author{\IEEEauthorblockN{Jos\'e~V.~de~M.~Cardoso,~Wamberto~J.~L.~Queiroz,}
-        \IEEEauthorblockN{~Paulo~R.~Lins~J\'unior,~and~Marcelo~S.~Alencar,~\textit{IEEE Senior Member}}
+\author{\IEEEauthorblockN{Jos\'e~V.~de~M.~Cardoso,~Paulo~R.~Lins~J\'unior,}
+        \IEEEauthorblockN{~Wamberto~J.~L.~Queiroz,~and~Marcelo~S.~Alencar,~\textit{IEEE Senior Member}}
 \IEEEauthorblockA{Universidade Federal de Campina Grande\\
@@
     applicability of \texttt{maoud} using examples in scenarios of communications
-    channels impaired by generalized fading, namely: spectrum sensing, bit error
-    rate computation, and fading estimation. For the latter, we develop an iterative
-    algorithm using the Majorization-Minimization framework, which allows reliable
-    estimation of the fading parameter. The development of \texttt{maoud} is open
-    source and its code, along with the code for the examples presented in this
-    paper, are avaliable at \texttt{http://github.com/mirca/maoud}.
+    channels impaired by generalized fading, namely: spectrum sensing and bit error
+    rate computation. The development of \texttt{maoud} is open source and its code,
+    along with the code for the examples presented in this paper, are avaliable at
+    \texttt{http://github.com/mirca/maoud}.
 \end{abstract}
@@
 \subsection*{Notation}
-Scalars and random variables are denoted as italic, small-case letters
-\textit{e.g.} $x$; sets and events are denoted as italic, capital
-letters \textit{e.g.}, $A$; vectors and random vectors are denoted as
-italic, boldface, small-case letters \textit{e.g.} $\bm{x}$. The $n-$th
-component of a vector $\bm{x}$ is denoted as $x_n$. A complex vector of length
-$n$ is defined as $\bm{x} \in \mathbb{C}^{n\times 1}$. All vectors are column
-vectors. Matrices are denoted as italic, boldface, capital letters as
-in $\bm{X}$; the identity matrix of order $n$ is denoted as $\bm{I}_n$. We
-define a discrete-time circularly symmetric Gaussian process $\bm{z}$ as any
-collection of random variables $\bm{z}~=~\bm{x}~+~j\bm{y}$,
-$j \triangleq \sqrt{-1}$, such that $\bm{x}$ and $\bm{y}$ are i.i.d. jointly
-Gaussian, with zero mean vector and covariance matrix given by
-$\mathbb{E}\left(\bm{z}\bm{z}^{\dagger}\right)$, in which $\bm{z}^\dagger$ means
-the conjugate transpose of $\bm{z}$. The expectation value with respect to the
-probability distribution of a random variable $x$ is denoted as $\mathbb{E}_x$.
-The probability of an event $A$ is denoted as $\mathbb{P}(A)$. The indicator
-function is denoted as $\mathbb{I}(\cdot)$, it evaluates to one if its argument
-is true and zero otherwise. For any given two real functions $f$ and $g$ defined
-on the same domain $D$, $f \cong g$ means that there exist a constant $c$ such that
-$f(\bm{x}) = g(\bm{x}) + c$, $\forall~ \bm{x} \in D$. The natural logarithm of a
-scalar $x > 0$ is denoted as $\log x$.
 

### 2018-05-14 paper/manuscript.tex
update paper

@@
-\documentclass[conference, 10pt]{IEEEtran}
-\usepackage[cmex10]{amsmath}
+\documentclass{sbrt2013port}
+%\usepackage[brazil]{babel}
+\usepackage{amsmath}
 \usepackage{amssymb}
@@
 \usepackage{color}
-\usepackage{placeins}
+%\usepackage{placeins}
 \usepackage{bm}
-\usepackage{cite}
+%\usepackage{cite}
 %\usepackage{stfloats}
-\usepackage{float}
+%\usepackage{float}
 \usepackage{hyperref}
-\usepackage{cite}
+%\usepackage{cite}
 \usepackage{tabularx,colortbl}
-\DeclareMathOperator*{\argmin}{arg\,min}
 
 \begin{document}
-\title{\texttt{maoud}: a Python package for Simulating Generalized Fading Channels}
 
-\author{\IEEEauthorblockN{Jos\'e~V.~de~M.~Cardoso,~Paulo~R.~Lins~J\'unior,}
-        \IEEEauthorblockN{~Wamberto~J.~L.~Queiroz,~and~Marcelo~S.~Alencar,~\textit{IEEE Senior Member}}
-\IEEEauthorblockA{Universidade Federal de Campina Grande\\
-Instituto Federal de Educa\c c\~ao, Ciencia, e Tecnologia da Para\'iba\\
-Campina Grande, Para\'iba, Brasil\\
-\{josevinicius, wamberto, paulo, malencar\}@iecom.org.br\\}
-}
+\title{Simulating Generalized Fading Channels in Python}
+
+\author{José Vinícius de M. Cardoso$^1$,   Paulo Ribeiro Lins Júnior$^2$, Wamberto Queiroz$^1$ e Marcelo Sampaio de Alencar$^3$
+\thanks{\noindent Instituto de Estudos Avançados em Comunicações -- Iecom; $^1$Universidade Federal de Campina Grande -- UFCG; $^2$Grupo de Pesquisa em Comunicações e Processamento de Informação -- GComPI/Instituto Federal de Educação, Ciência e Tecnologia da Paraíba -- IFPB, Campus Campina Grande -- PB, $^3$Universidade Federal da Bahia -- UFBA, emails: $^1$\{josevinicius, wamberto\}@iecom.org.br, $^2$paulo.lins@ifpb.edu.br e $^3$malencar@iecom.org.br.}}
 
@@
 
+\markboth{XXXVI SIMPÓSIO BRASILEIRO DE TELECOMUNICAÇÕES E PROCESSAMENTO DE SINAIS - SBrT'2018, 16-19 DE SETEMBRO DE 2018, CAMPINA GRANDE, PB} {XXXVI SIMPÓSIO BRASILEIRO DE TELECOMUNICAÇÕES E PROCESSAMENTO DE SINAIS - SBrT'2018, 16-19 DE SETEMBRO DE 2018, CAMPINA GRANDE, PB}
+
 \begin{abstract}
-    We present a well tested Python-based library for simulating and computing
-    generalized fading channels, named \texttt{maoud}. We describe the
-    applicability of \texttt{maoud} using examples in scenarios of communications
-    channels impaired by generalized fading, namely: spectrum sensing and bit error
-    rate computation. The development of \texttt{maoud} is open source and its code,
-    along with the code for the examples presented in this paper, are avaliable at
+    We present a novel and well tested Python-based library for simulating and computing
+    generalized fading channels, considering $\alpha\text{-}\mu$, $\kappa\text{-}\mu$, and
+$\eta\text{-}\mu$ distributions. We describe the
+    applicability of this library using a few communications channels scenarios
+    impaired by generalized fading, namely, spectrum sensing and bit error
+    rate computation. The development of the library is open source and its code along
+    with examples are available at
     \texttt{http://github.com/mirca/maoud}.
@@
 
-\IEEEpeerreviewmaketitle
+\begin{keywords}
+Generalized Fading, Simulation, Python
+\end{keywords}
+
 \section{Introduction}
@@
 the generation of samples following these distributions is usually
-a time-consuming task. In~\cite{cogliatti2012}, the authors built an efficient
+a time-consuming task.
+
+In~\cite{cogliatti2012}, the authors built an efficient
 algorithm, based on the rejection method, for generation of samples from those
-distributions.
-
-however, there are neither open nor
+distributions. However, there are neither open nor
 closed source implementations available to the scientific community.
 
-In this paper, we present an open source Python package, named \texttt{maoud},
+In this paper, we present an open source Python package
 for generation of samples following the $\alpha\text{-}\mu$, $\kappa\text{-}\mu$, and
-$\eta\text{-}\mu$ distributions. The usefullness of $\texttt{maoud}$ is illustrated
-through examples involving spectrum sensing, bit error rate (BER) computation, and
-fading estimation.
+$\eta\text{-}\mu$ distributions. The usefullness of ths package is illustrated
+through well known examples involving spectrum sensing and bit error rate (BER) computation.
 
-\subsection*{Notation}
+Section~\ref{rejec} presents the well known rejection method which is used as
+the basis for the proposed implementation. Section~\ref{sensing} and~\ref{ber}
+demonstrates the features of the proposed package in spectrum sensing over complex
+generalized fading channels and bit error rate computation on $\alpha$-$\mu$ fading.
+Section~\ref{conclusions} states the final remarks.
 
-\section{Rejection sampling}
+\section{Rejection Sampling}\label{rejec}
 
-\section{Examples}
-\subsection{Spectrum Sensing in Complex Generalized Fading Channels}
+The algorithm implemented in this work, originally proposed in~\cite{cogliatti2012},
+is based on the rejection method, which is one of the most used for the generation
+of samples of a probability distribution.
+
+We briefly describe the algorithm as follows. Consider that we would like to simulate a
+random variable $x$ with a probability density $f$. The basic idea is to find
+an alternative probability density $g$, from which there exists an efficient procedure
+to generate samples, e.g., inverse methods. Additionally, it is required that $g$
+majorizes $f$, i.e., we assume that there exists a real number $c$ such that $f(x)/g(x) < c$.
+
+Basically, the steps of the rejection algorithm are\cite{ross}:
+\begin{enumerate}
+	\item generate a sample $y$ from the probability density $g$;
+    \item generate a sample $u$ from a uniform density with support $(0, 1)$;
+	\item check $u \leq \frac{f(y)}{cg(y)}$; if true then accept $y$; otherwise, return to step 1.
+\end{enumerate}
+
+The implementation of this algorithm along with the code to efficiently generate
+samples from the $\alpha$-$\mu$, $\eta$-$\mu$, and $\kappa$-$\mu$ distributions
+is available at \url{http://github.com/mirca/maoud}.
+
+In order to validate the implementation, we apply the routines to
+two use cases in wireless communications: spectrum sensing and bit error rate computation.
+
+\section{Spectrum Sensing in Complex Generalized Fading Channels}~\label{sensing}
 
@@
 \begin{align}
-    H_0:~& \bm{y} = \bm{w},\\
-    H_1:~& \bm{y} = h\bm{s} + \bm{w},
+    H_0:  \bm{y} &= \bm{w},\\
+    H_1:  \bm{y} &= h\bm{s} + \bm{w},
 \end{align}
-in which $\bm{y} \in \mathbb{C}^{n\times 1}$ is the received vector signal,
+\noindent in which $\bm{y} \in \mathbb{C}^{n\times 1}$ is the received vector signal,
 $\bm{w} \in \mathbb{C}^{n\times 1}$ is complex Gaussian noise process with zero mean
@@
 \end{equation}
-in which $\delta$ is a strictly positive real number known as energy threshold,
-and $d_\delta (\tilde{y}) = j,~j \in \{0,1\}$, means that the detector has decided
-in favor of the hypothesis $H_j$.
+in which $\mathbb{I}$ is the indicator function, $\delta$ is a strictly positive real
+number known as energy threshold, and $d_\delta (\tilde{y}) = j,~j \in \{0,1\}$,
+means that the detector has decided in favor of the hypothesis $H_j$.
 
@@
 Characteristic (ROC), which consists in varying $\delta$ and computing the pairs of
-probability of false alarm and miss detection, as illustrated in Fig.~\ref{fig:spectrum-sensing}.
+probability of false alarm and miss detection, as illustrated in Fig.~\ref{fig:spectrum-sensing}, in which the solid curve represents the theorectical probabilities as stated on
+(\ref{eq:pf}) and (\ref{eq:pd}) for different values of
+$\delta$, whereas bullets represent Monte Carlo simulations acquired with $10^6$ realizations.
+The input signal $\bm{s}$ consists in a vector of length $n=25$ in which each entry represents
+a symbol of a 64-PSK constellation. Symbols are assumed to be equiprobable and
+the signal-to-noise ratio is set to $5$ dB.
 
@@
     \centering
-    \includegraphics{figures/spectrum_sensing.eps}
+    \includegraphics{figures/spectrum_sensing}
     \caption{Receiver Operating Characteristic for the energy detector in $\alpha$-$\mu$
-             fading channel with $\alpha=2$ and $\mu=1$, i.e., Nakagami-$m$, $m = 1$.
-             The solid curve represents the theorectical probabilities as stated on
-             (\ref{eq:pf}) and (\ref{eq:pd}) for different values of
-             $\delta$, whereas bullets represent Monte Carlo simulations acquired with $10^6$ realizations.
-             The input signal $\bm{s}$ consists in a vector of length $n=25$ in which each entry represents
-             a symbol of a 64-PSK constellation. Symbols are assumed to be equiprobable.
-             The signal-to-noise ratio is set to $5$ dB.}
+             fading channel with $\alpha=2$ and $\mu=1$.
+             }
     \label{fig:spectrum-sensing}
@@
 
-\subsection{BER in $\alpha$-$\mu$ Fading}
+\section{Bit Error Rate in $\alpha$-$\mu$ Fading}~\label{ber}
 
@@
 
+Fig.~\ref{fig:ber} shows the expression of the BER as a function of the signal-to-noise ratio.
+As we can see, the simulation presents an excellent agreement against theorectical results.
+
 \begin{figure}[!htb]
     \centering
-    \includegraphics{figures/ber.eps}
-    \caption{BER}
+    \includegraphics{figures/ber}
+    \caption{BER \textit{versus} SNR.}
     \label{fig:ber}
@@
 
-\section{Conclusions}
+\section{Conclusions}\label{conclusions}
+
+This paper presents a novel Python-based library for generalized fading simulation.
+The implementation is tested and validated in two use cases, namely,
+spectrum sensing and BER computation.
+
+The computational results show that the implementation presents a
+satisfactory agreement when compared with the theorectical formulation.
+
+We expect that the proposed library, which is open source,
+will be usefull to researchers, professors, and students of
+the field of wireless communications.
 
 \bibliographystyle{IEEEtran}
-\bibliography{manuscript.bib}
+\bibliography{manuscript}
 

### 2018-05-14 maoud/distributions.py
update readme

@@ -158,6 +158,7 @@ class ComplexAlphaMu(ComplexDistribution):
     def envelope_pdf(self, x):
         return AlphaMu(self.alpha, self.mu).pdf(x)
 
+
 class ComplexEtaMu(ComplexDistribution):
     def __init__(self, eta, mu):
         self.eta = eta

### 2018-05-14 maoud/sampling.py
improve docs

@@ -3,8 +3,7 @@ import math
 
 def rejection_sampling(pdf, x, n_samples, *args):
     """
-    This is actually a pretty good implementation of the acceptance-rejection
-    sampler.
+    This is maybe the simplest implementation of the acceptance-rejection sampler.
 
     Parameters
     ----------
@@ -21,6 +20,9 @@ def rejection_sampling(pdf, x, n_samples, *args):
     -------
     accepted_samples : array
         Array containing samples from ``pdf``
+    acceptance_fraction : float
+        The mean ratio between the number of accepted samples and
+        the number of generated ones.
     """
     pdf_x = pdf(x, *args)
     pdf_min, pdf_max  = np.min(pdf_x), np.max(pdf_x)

### 2018-05-14 docs/source/conf.py
generate docs

@@ -1,0 +1,177 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+#
+# maoud documentation build configuration file, created by
+# sphinx-quickstart on Fri Nov 17 08:53:26 2017.
+#
+# This file is execfile()d with the current directory set to its
+# containing dir.
+#
+# Note that not all possible configuration values are present in this
+# autogenerated file.
+#
+# All configuration values have a default; values that are commented out
+# serve to show the default.
+
+# If extensions (or modules to document with autodoc) are in another directory,
+# add these directories to sys.path here. If the directory is relative to the
+# documentation root, use os.path.abspath to make it absolute, like shown here.
+#
+# import os
+# import sys
+# sys.path.insert(0, os.path.abspath('.'))
+
+# -- General configuration ------------------------------------------------
+
+# If your documentation needs a minimal Sphinx version, state it here.
+#
+# needs_sphinx = '1.0'
+
+# Add any Sphinx extension module names here, as strings. They can be
+# extensions coming with Sphinx (named 'sphinx.ext.*') or your custom
+# ones.
+extensions = ['sphinx.ext.autodoc',
+    'sphinx.ext.autosummary',
+    'sphinx.ext.doctest',
+    'sphinx.ext.intersphinx',
+    'sphinx.ext.todo',
+    'sphinx.ext.coverage',
+    'sphinx.ext.mathjax',
+    'sphinx.ext.ifconfig',
+    'sphinx.ext.viewcode',
+    'sphinx.ext.githubpages',
+    'sphinx.ext.graphviz',
+    'sphinx.ext.inheritance_diagram',
+    'numpydoc',
+    'nbsphinx']
+
+# Add any paths that contain templates here, relative to this directory.
+templates_path = ['_templates']
+
+# The suffix(es) of source filenames.
+# You can specify multiple suffix as a list of string:
+#
+# source_suffix = ['.rst', '.md']
+source_suffix = '.rst'
+
+# The master toctree document.
+master_doc = 'index'
+
+# General information about the project.
+project = 'maoud'
+copyright = '2018, mirca'
+author = 'mirca'
+
+# The version info for the project you're documenting, acts as replacement for
+# |version| and |release|, also used in various other places throughout the
+# built documents.
+#
+# The short X.Y version.
+version = '0.1dev0'
+# The full version, including alpha/beta/rc tags.
+release = '0.1dev0'
+
+# The language for content autogenerated by Sphinx. Refer to documentation
+# for a list of supported languages.
+#
[…]

### 2018-05-14 docs/source/conf.py
update gh-pages

@@ -1,177 +1,0 @@
-#!/usr/bin/env python3
-# -*- coding: utf-8 -*-
-#
-# maoud documentation build configuration file, created by
-# sphinx-quickstart on Fri Nov 17 08:53:26 2017.
-#
-# This file is execfile()d with the current directory set to its
-# containing dir.
-#
-# Note that not all possible configuration values are present in this
-# autogenerated file.
-#
-# All configuration values have a default; values that are commented out
-# serve to show the default.
-
-# If extensions (or modules to document with autodoc) are in another directory,
-# add these directories to sys.path here. If the directory is relative to the
-# documentation root, use os.path.abspath to make it absolute, like shown here.
-#
-# import os
-# import sys
-# sys.path.insert(0, os.path.abspath('.'))
-
-# -- General configuration ------------------------------------------------
-
-# If your documentation needs a minimal Sphinx version, state it here.
-#
-# needs_sphinx = '1.0'
-
-# Add any Sphinx extension module names here, as strings. They can be
-# extensions coming with Sphinx (named 'sphinx.ext.*') or your custom
-# ones.
-extensions = ['sphinx.ext.autodoc',
-    'sphinx.ext.autosummary',
-    'sphinx.ext.doctest',
-    'sphinx.ext.intersphinx',
-    'sphinx.ext.todo',
-    'sphinx.ext.coverage',
-    'sphinx.ext.mathjax',
-    'sphinx.ext.ifconfig',
-    'sphinx.ext.viewcode',
-    'sphinx.ext.githubpages',
-    'sphinx.ext.graphviz',
-    'sphinx.ext.inheritance_diagram',
-    'numpydoc',
-    'nbsphinx']
-
-# Add any paths that contain templates here, relative to this directory.
-templates_path = ['_templates']
-
-# The suffix(es) of source filenames.
-# You can specify multiple suffix as a list of string:
-#
-# source_suffix = ['.rst', '.md']
-source_suffix = '.rst'
-
-# The master toctree document.
-master_doc = 'index'
-
-# General information about the project.
-project = 'maoud'
-copyright = '2018, mirca'
-author = 'mirca'
-
-# The version info for the project you're documenting, acts as replacement for
-# |version| and |release|, also used in various other places throughout the
-# built documents.
-#
-# The short X.Y version.
-version = '0.1dev0'
-# The full version, including alpha/beta/rc tags.
-release = '0.1dev0'
-
-# The language for content autogenerated by Sphinx. Refer to documentation
-# for a list of supported languages.
-#
[…]

### 2018-05-14 maoud/__init__.py

@@ -1,3 +1,0 @@
-from .distributions import *
-from .sampling import *
-from .utils import *

### 2018-05-14 maoud/distributions.py

@@ -1,197 +1,0 @@
-from abc import ABC, abstractmethod
-import numpy as np
-import math
-import scipy.special as sps
-import scipy.stats as stats
-from .sampling import rejection_sampling
-
-
-class Distribution(ABC):
-    """An abstract class for a probability distribution.
-    """
-    @abstractmethod
-    def pdf(self, x):
-        """Defines a 1D probability density function.
-
-        Parameters
-        ----------
-        x : 1darray
-            Points where to evaluate the pdf.
-
-        Returns
-        -------
-        pdf : 1darray
-            pdf values at `x`.
-        """
-        pass
-
-    def rvs(self, x, size):
-        """Returns a sample of length `size` in the range
-        [x.min(), x.max()].
-
-        Parameters
-        ----------
-        x : array
-            The support of the pdf.
-        size : int
-            Size of the sample (number of realizations).
-        """
-        return rejection_sampling(self.pdf, x, size)[0]
-
-
-class ComplexDistribution(Distribution):
-    """Defines a class for probability distribution
-    arising from a complex random variable Z = X + jY,
-    where j = sqrt(-1).
-    """
-    def rvs(self, x, y, size):
-        """Returns a sample of length `size` in the range
-        [x.min(), x.max()] and [y.min(), y.max()] for the
-        real and imaginary parts.
-
-        Parameters
-        ----------
-        x, y : arrays
-            The support of the pdf of the real and imaginary parts,
-            respectively.
-        size : int
-            Size of the sample (number of realizations).
-        """
-        if len(x) != len(y):
-            raise ValueError("x and y must have the same length.")
-
-        return (rejection_sampling(self.pdf, x, size)[0]
-                + 1j * rejection_sampling(self.pdf, y, size)[0])
-
-    def envelope_pdf(self, x):
-        pass
-
-
-class AlphaMu(Distribution):
-    """Defines the α — μ probability distribution.
-    For the theorectical aspects of the α — μ distribution, see
-    M. D. Yacoub, The α — μ distribution: A physical fading model for the Stacy
[…]

### 2018-05-14 maoud/sampling.py

@@ -1,45 +1,0 @@
-import numpy as np
-import math
-
-def rejection_sampling(pdf, x, n_samples, *args):
-    """
-    This is maybe the simplest implementation of the acceptance-rejection sampler.
-
-    Parameters
-    ----------
-    pdf : callable
-        The analytical formulation of the density function to get samples from.
-    x : array
-        The support of the pdf.
-    n_samples : int
-        The sample size.
-    args : list
-        List of additional arguments to be passed to ``pdf``.
-
-    Returns
-    -------
-    accepted_samples : array
-        Array containing samples from ``pdf``
-    acceptance_fraction : float
-        The mean ratio between the number of accepted samples and
-        the number of generated ones.
-    """
-    pdf_x = pdf(x, *args)
-    pdf_min, pdf_max  = np.min(pdf_x), np.max(pdf_x)
-
-    if not np.isfinite(pdf_max):
-        raise ValueError("pdf has nan or inf values.")
-
-    n_samples = int(n_samples)
-    x_min, x_max = np.min(x), np.max(x)
-    accepted_samples = []
-    acceptance_fraction = []
-
-    while len(accepted_samples) < n_samples:
-        unif_x = np.random.uniform(low=x_min, high=x_max, size=n_samples)
-        unif_y = np.random.uniform(low=pdf_min, high=pdf_max, size=n_samples)
-        accept = unif_y <= pdf(unif_x, *args)
-        accepted_samples = np.concatenate([accepted_samples, unif_x[accept]])
-        acceptance_fraction = np.concatenate([acceptance_fraction, [np.sum(accept)/n_samples]])
-
-    return accepted_samples[:n_samples], acceptance_fraction

### 2018-05-14 maoud/utils.py

@@ -1,39 +1,0 @@
-import numpy as np
-import scipy.stats as stats
-
-def marcumq(x, df, nc):
-    """Computes the Marcum-Q function.
-
-    Parameters
-    ----------
-    x : input array
-        The points where to evaluate the Marcum-Q function.
-    df : int
-        The degrees of freedom.
-    nc : float
-        The non-centrality parameter.
-
-    Returns
-    -------
-    y : output array
-        Array containing the values of the Marcum-Q function
-        evaluated at `x`.
-    """
-
-    return stats.ncx2.sf(x*x, 2*df, nc*nc)
-
-def mpsk(M, size):
-    """Generates a random sample of symbols from a normalized M-PSK
-    constellation.
-
-    Parameters
-    ----------
-    M : int
-        Order of the constellation.
-    size : int
-        Number of symbols to generate.
-    """
-
-    constellation = np.exp(1j * np.linspace(-np.pi / 4, 7 * np.pi / 4 - 2 * np.pi / M, M)) / np.sqrt(M)
-    symbols = np.random.random_integers(0, M-1, size)
-    return constellation[symbols]

### 2018-05-14 setup.py

@@ -1,41 +1,0 @@
-#!/usr/bin/env python
-import sys
-from setuptools import setup
-# To use a consistent encoding
-from codecs import open
-import os
-from os import path
-
-# Prepare and send a new release to PyPI
-if "release" in sys.argv[-1]:
-    os.system("python setup.py sdist")
-    os.system("twine upload dist/*")
-    os.system("rm -rf dist/maoud*")
-    sys.exit()
-
-here = path.abspath(path.dirname(__file__))
-
-# Get the long description from the README file
-with open(path.join(here, 'README.rst'), encoding='utf-8') as f:
-    long_description = f.read()
-
-setup(
-    name='maoud',
-    packages=['maoud'],
-    version='0.1.dev0',
-    description='Simulating generalized fading channels',
-    long_description=long_description,
-    url='https://github.com/mirca/maoud',
-    author='mirca',
-    author_email='jvmirca@gmail.com',
-    license='MIT',
-    classifiers=[
-        'Development Status :: 3 - Alpha',
-        'Intended Audience :: Science/Research',
-        'License :: OSI Approved :: MIT License',
-        'Programming Language :: Python :: 3.6',
-    ],
-    tests_require=['pytest', 'pytest-cov'],
-    keywords='statistics probability',
-    install_requires=['numpy', 'scipy', 'tensorflow']
-)

### 2018-09-13 paper/manuscript.tex
minor corrections

@@
 \begin{abstract}
-    We present a novel and well tested Python-based library for simulating and computing
-    generalized fading channels, considering $\alpha\text{-}\mu$, $\kappa\text{-}\mu$, and
-$\eta\text{-}\mu$ distributions. We describe the
-    applicability of this library using a few communications channels scenarios
-    impaired by generalized fading, namely, spectrum sensing and bit error
-    rate computation. The development of the library is open source and its code along
-    with examples are available at
+    We present a novel and well tested Python-based library for simulating and
+    computing generalized fading channels considering $\alpha\text{-}\mu$,
+    $\kappa\text{-}\mu$, and $\eta\text{-}\mu$ distributions. We describe the
+    applicability of this library through common communications engineering
+    use cases such as spectrum sensing and bit error rate computation.
+    The development of the library is open source and its code, along with
+    examples, are available at
     \texttt{http://github.com/mirca/maoud}.
@@
 By fading channel simulation, we refer to the generation of samples from a probability distribution
-that resembles the effects and impairments caused by real communications fading channels on the
+that resembles the effects and impairments caused by real communications channels on the
 transmitted signal.
@@
 for generation of samples following the $\alpha\text{-}\mu$, $\kappa\text{-}\mu$, and
-$\eta\text{-}\mu$ distributions. The usefullness of ths package is illustrated
-through well known examples involving spectrum sensing and bit error rate (BER) computation.
-
-Section~\ref{rejec} presents the well known rejection method which is used as
-the basis for the proposed implementation. Section~\ref{sensing} and~\ref{ber}
-demonstrates the features of the proposed package in spectrum sensing over complex
-generalized fading channels and bit error rate computation on $\alpha$-$\mu$ fading.
-Section~\ref{conclusions} states the final remarks.
+$\eta\text{-}\mu$ distributions. The usefullness of this package is illustrated
+through well known examples involving spectrum sensing and bit error rate
+(BER) computation.
 
@@
 
-Basically, the steps of the rejection algorithm are\cite{ross}:
+Basically, the steps of the rejection algorithm are~\cite{ross}:
 \begin{enumerate}
@@
         1 -  P(\delta | H_0) = 1 - \gamma\left(n, \frac{\delta}{\sigma^2}\right),\label{eq:pf} \\
-    \mathbb{P}\left(d_\delta(\tilde{y}) = 0 | H_1\right) &= \mathbb{E}_{h}\left(P(\delta| h, H_1)\right)\nonumber\\
-    &= \int_{-\infty}^{+\infty} P(\delta | h, H_1)p(h)\;\mathrm{d}h,\label{eq:pd}
+    \mathbb{P}\left(d_\delta(\tilde{y}) = 0 | H_1\right) & = \int_{-\infty}^{+\infty} P(\delta | h, H_1)p(h)\;\mathrm{d}h,\label{eq:pd}
 \end{align}
@@
     \caption{Receiver Operating Characteristic for the energy detector in $\alpha$-$\mu$
-             fading channel with $\alpha=2$ and $\mu=1$.
+             channel with $\alpha=2$ and $\mu=1$.
              }
@@
 in which $s \in \{0, a\}$, $a \in \mathbb{R}_{+}$, is a transmitted signal,
-$h$ is an $\alpha$-$\mu$ random variable and $\bm{w}$ is a Gaussian random variable
+$h$ is an $\alpha$-$\mu$ random variable and $w$ is a Gaussian random variable
 with zero mean vector and variance $\sigma^2$, and $y$ is the received signal.
@@
 \begin{align}
-    \mathbb{P}\left(\hat{y} = 1 | s = 0\right) & = \mathbb{P}\left(|w - a|^2 - |w|^2 < 0\right)\nonumber\\
-    & = \mathbb{P}\left(w > \frac{a}{2}\right) = 1 - \Phi\left(\frac{a}{2\sigma}\right)
+    \mathbb{P}\left(\hat{y} = 1 | s = 0\right) & = \mathbb{P}\left(|w - a|^2 - |w|^2 < 0\right) = 1 - \Phi\left(\frac{a}{2\sigma}\right)
 \end{align}
@@
 \begin{align}
-    \mathbb{P}\left(\hat{y} = 0 | s = a\right) & = \mathbb{P}\left(ha + w < \frac{a}{2}\right) \nonumber\\
-    & = \mathbb{E}_h\left(\Phi\left(\frac{a(1 - 2h)}{2\sigma}\right)\right).
+    \mathbb{P}\left(\hat{y} = 0 | s = a\right) & = \mathbb{P}\left(ha + w < \frac{a}{2}\right) = \mathbb{E}_h\left(\Phi\left(\frac{a(1 - 2h)}{2\sigma}\right)\right).
 \end{align}
 
-Fig.~\ref{fig:ber} shows the expression of the BER as a function of the signal-to-noise ratio.
+In Fig.~\ref{fig:ber}, we show the expression of the BER as a function of the signal-to-noise ratio,
+for the system under consideration with $\alpha=2$ and $\mu = 5$.
 As we can see, the simulation presents an excellent agreement against theorectical results.
-
 \begin{figure}[!htb]
@@
     \includegraphics{figures/ber}
-    \caption{BER \textit{versus} SNR.}
+    \caption{BER as a function of the SNR for $\alpha=2$ and $\mu = 5$}
     \label{fig:ber}
@@
 
+Finally, all the simulations were done in a personal laptop,
+and the generation of $10^6$ samples from any of the generalized fading
+distributions took on average 10 seconds.
+
 \bibliographystyle{IEEEtran}
